Rebecca telling her story:

I was a very healthy, fit 120 lbs, strong (former athlete), woman. I walked 5
miles a day, did yoga and have taken significant supplements to aid my arthritis
and old gymnastics spinal injuries unmedicated. These have helped enormously
with my overall health.

The night of my first Pfizer Vaccine, August 24th 2021, I had an Anaphylactic
Shock reaction, alone at home. Unable to breathe, with acute asthmatic symptoms
and I didn’t think I’d survive the night. A wheezy cough began immediately as
well, and still plagues me today, although now I have been prescribed cough
pills strong enough to manage it.

I was prescribed Albuteral inhaler initially, the next day after my shot and
needed to use it around 10X a day, and went through far more than insurance
would cover. I told my doctor all the symptoms I was suffering, however none of
this is recorded in my medical record or with VAERS. With numerous other
symptoms I could not get my general practitioner of 20+ years to respond to my
calls or emails about what was happening to me. Finally, last week a new
physician prescribed another inhaler, far stronger with heavy cortisone content
that is finally working so I can breathe more easily, and also requested chest
x-rays.

The chest x-rays revealed Pneumonia. So I now am on an antibiotic for that.

Many days I now feel pretty good. But fatigue, body aches, and acute pain of all
my arthritic locations began within weeks of the shot. I take no pain meds, so
have had to cope with that with yoga, meditation and prayer.

As a happy, healthy professional, with 2 grown daughters, this has been a
horrifying experience. I reported this to my employer, and they really did not
care although I was an Executive, and was usually listened to.

THE LEAD UP TO THE VACCINE...

Under chronic pressure from my employer every Monday morning (our CEO leads a
meeting), we were pressured to get vaccinated, against our will. We were treated
like we were idiots for not getting it. I work from home, alone most days, and
in sales so occasional outings for lunches were not putting me at any great
risk. I’m in Silicon Valley, Santa Clara County, the most abusive lock-down
county in the US, with ongoing mask requirements even today.

Early October my employer let me go without explanation, as I refused the 2nd
Pfizer shot. No letter of explanation, just fired over the phone, as a top
performer. It has been surreal to say the least. I’ve lost my job, and want to
get out of California and work as a Journalist again (my former career as I have
a Journalism degree), in a “free” state. I want this story told and feel so
passionate about all this as to never want to return to the corporate world,
where this unconstitutional Tyranny is being enforced, and there isn’t even a
law nor an EO to cover this disgraceful Genocide and the related issues around
it all.

I lost my job in an 18 year career as an executive, not wanting the 2nd shot. I
was fired for no documented reason by the CFO. I asked why, and he vaguely gave
a non-answer.

I have chronic asthma now and fatigue, frequently ache and feel sick.

The media are covering this up. I posted this fact. I posted your content of the
VAERS report showing 17,000 deaths.

“Do not get this Vax” is my message. No job or money is worth it, but I broke
down under job pressure. I deeply regret it as I had excellent health prior, but
I will make my way back, someday.

I am honored to share my story, as I want to make a difference before it’s too
late. Our children are going to be stuck here in Vax Tyranny, being disabled and
injured, long after we’re gone if this ‘Reign of Terror’ continues.

