Nadine’s story in her own words on 2nd Nov 2021:

Ten minutes after the shot my hand went numb. Two hours later my feet went
numb. Woke up at 3am with chest pain. Went to work one hour later with shooting
pains in my head, extreme dizziness, losing balance and falling. Very confused
about where I was and what to do next. Profuse sweating. Called 811 and told the
nurse what was happening. She told me to go to hospital right away.

Got to Emergency and explained symptoms. They gave me a chest x-ray and blood
tests. Those were clear so sent me home. I asked about the shooting head pains
and they told me they didn’t want to subject me to anymore radiation that
day. Asked about chest pain. Nope we don’t need to do ECG because your blood is
ok. And the numbness? No answer. Told me to come back if the chest pain was
crushing.

Went home to sleep. Very sharp pain in my head. Felt like something moved and
jolted me awake. So dizzy and weak, I could not get out of bed. When I did get
up my legs were trembling and was hard to walk. Over the next two weeks the
numbness turned to pins and needles. It is now in both hands and from feet to
hips. I get shooting pains in my legs and hands. Pins and needles have now
started on left side of face.

It has been over a month and I still have chest pain and the pains in my
head. The pins and needles are getting stronger. Some days it feels like my
whole body is vibrating and some days it is slight tremors. Headaches every day,
some mild, some migraine. Still have moments of extreme dizziness.

My Doctor just sent me for an ECG on Friday. He says I was panicking. No way
will any of them admit it was the Pfizer Vaccination.

I am so angry and frustrated.

My heart goes out to all of you that have either lost someone or are dealing
with vaccine injuries.
