My entire life, I’ve been perfectly fine and healthy and early this year, I
started working at a dental clinic and was asked to get the vaccine. This was
before they suggested the age limits for the AstraZeneca, and so on April 2nd, I
was given my first dose of AstraZeneca.

Initially, I had the common side effects - painful arm, headache etc. but the
next day (April 3rd), I fainted and was taken to hospital. While in hospital, we
realised that I couldn’t walk. I was having tremors all over my body and
couldn’t hold myself up or balance.

I was discharged from 2 Hospitals still in terrible condition, saying that this
was due to mental illness and completely unrelated to the vaccine. I tried to
talk to my doctors, telling them that I do not have any mental illnesses and
that I was perfectly fine before I had taken the vaccine. But I was dismissed by
every doctor and told that it was a form of attention seeking. My parents had no
idea what was happening and I was still shaking with tremors and unable to
walk.

So my parents tried a third hospital. I was in hospital in the neurology ward
for 2 weeks and was then transferred to a rehabilitation hospital where I spent
around 2 months as an inpatient. I continue to go to rehab during the day and
have been told that recovery and gaining full mobility will most probably take
around a year.

I have been privileged enough to have never had any negative experiences with
doctors or hospitals in the past UP UNTIL THIS POINT. Every single doctor and
neurologist I have encountered during this time with my reaction has dismissed
me and treated me like a patient with some sort of mental illness, despite me
telling them that this was post vaccine. They so quickly defend the vaccine
without even listening to me. They were rude and condescending and they put it
on anxiety and depression as the cause. I had psych evaluation which came back
completely normal and they eventually put it to “unknown causes, unrelated to
the vaccine”.

Before having this vaccine, I was a normal teenage girl going to Uni, meeting up
with friends and spending time with family. And now the day after my vaccine,
I’m unable to walk with tremors all over and now i’m on a wheelchair and have to
go to rehab for at least a year.

Doctors still say it’s a coincidence but I don’t think so at all. We have
reported this as a side effect but not sure what’s happening with that. NSW
Health has even contacted me to get my second dose, which I obviously
refused.

I’ve read a bit about neurological side effects after the vaccine and I’ve
finally got the courage to share what I’ve been through during the last 3.5
months. I’ve still got a while to go recovery wise but I’ve been assured by
neurologists that with rehab for a couple of months, I should return back to
what I was!! Thanks for reading.

