Holly, age 34 Years old from Leeds UK, took the Pfizer Vaccine on 7th May 2021
which resulted in a Coma due to a Bleed on the Brain which resulted in Brain
Surgery. .

Holly was a Nursery Nurse in a primary school working with 2-year-old children
is a beautiful kind hearted soul and thought that by taking the vaccine this
would protect those around her, especially when working with children.

Five weeks after the vaccine Holly started to present with debilitation
headaches and sickness and then two weeks later on 18th July Holly collapsed and
got admitted to Leeds General Infirmary. The hospital confirmed, after doing an
MRI, that Holly had 4 blood clots in the right side of her brain.

Holly was sent for immediate Neuro Brain Surgery to remove the clots and a drain
inserted in her scull to remove the fluid built up from the brain swell.

Once out of surgery Holly was in a coma and remained in ICU. Holly was unable to
breath on her own and was intubated, although we have seen improvements and she
can now breath unaided, although she was fitted with a Tracheotomy.

To the family’s horror the hospital initially denied any visiting to see Holly
other than half an hour per week giving the explanation that this is
governmental directive due to Covid!

We urgently needed to raise funds for solicitors’ fees for the family to fight
the hospitals decision to enable them get the family on the ward and this legal
process was started and co-ordinated on 17th August by No More Silence. The
instruction fees were paid by No More Silence, although to fight this case
legally the costs will be much more.

When the family visited (half an hour visit) Holly squeezed her husband and her
sister’s hand, opened her eyes and stuck out her tongue under command. This had
not been seen by the hospital staff before the family had visited and it show
the families interaction in Holly’s recover was absolutely necessary.

