
I spent two days in the hospital with my son, May 19 \& 20th 2021. He was
diagnosed with Bilateral Pulmonary Embolisms and an Infarction in his left lung
from his Johnson \& Johnson Vaccine.

Six days later, May 26th, the back of my left leg was so sore I couldn’t walk on
it. My son dropped me off at the emergency room where I had blood taken and my D
Dimer was 101630 (Normal is 0-500). I had a Doppler Ultrasound and they found a
2.5 FOOT LONG DVT (blood clot) in my left leg. I was taken by ambulance to
another hospital to have it removed surgically.

They did a contrast CT at the next hospital and found Pulmonary Embolisms. Which
stopped the surgery. I spent a week in the hospital on a heparin drip and 7 days
after on tinzaperin injections. I am now on blood thinners for life.

I was back in the hospital a week later with a massive soft tissue infection in
my arm, armpit, breast and side. My symptoms started 19 days after Pfizer
Vaccination, but I was so distracted by my son, I didn’t have it treated until a
week later.

Since then I have been hospitalized for menstrual haemorrhage twice and now have
to possibly have a hysterectomy. I have an echocardiogram, holter monitor,
cardiology appointment, vascular surgery appointment, haematology appointment
and have been referred to urology for a kidney issue.

I live every day broken, both physically and mentally.

No one in the hospitals care about what happens to you if you don’t have
Covid. Not one of the Doctors treating me in hospital reported my injury!

I have since reported to Saskatchewan Health, where a local Medical Health
Officer denied my claim due to my sons injury and “suspected previous
undiagnosed blood disorder”. My haematologist is looking into appealing this
decision. I reported to Pfizer, which is obligated to report to Health
Canada. No response. I cannot apply for compensation because of the MHO denial
of my initial claim in June.
