Mary’s Story told by her Family

On May 20, 2021, our sister Mary Meade Ruth, 53, had completed her second dose
of the Moderna vaccine. She like many other Americans, was rolling up her sleeve
to help America get back on its feet and beat COVID. She never imagined when she
was heading home from her appointment that day, she would develop blood clots
from the vaccine. After all, Mary did not have any pre-existing conditions.

We are still in disbelief and shock, but Mary experienced complications after
her second Moderna shot and consequently suffered two “massive heart attacks”
that day. One at home in her kitchen, while eating dinner with her family. One
at the hospital. Mary flatlined both times and had to be revived. It was
estimated that during the initial heart attack, she had gone without oxygen for
as long as 3-7 minutes, before paramedics regained a pulse. Mary spent the next
36 hours battling for her life and endured a series of setbacks, as the doctors
and ICU nurses worked to stabilize her vitals and internal bleeding.

During this crisis, Mary’s life depended on around-the-clock care that only the
ICU could provide. Although Mary made incredible progress, progress the doctors
deemed miraculous, her ordeal and journey to recovery is far from over. She will
still require continued around-the-clock home care along with substantial
lifelong medical expenses.

Mary and her husband Bill are the most selfless and humble individuals we know;
always doing the right thing and always there to help others in need. Even
during this catastrophic life changing event, they have kept their sense of
humour and humility.

