Michael (Mike), a longtime resident of Gilroy, passed away on November 1,
2021. Never a kinder more gentle man did I know than my husband, Michael.

Mike was adamant that people know what happened to him, and what caused his
early and unexpected death.

Message from Mike:

“Many nurses and non-nursing staff begged me and my wife to get the truth out to
the public about the Covid-19 Vaccines because the truth of deaths from these
Vaccines is being hidden within the medical profession”.

“I promised I would get the message out, so, here is my message: I was afraid of
getting the vaccine for fear that I might die. At the insistence of my doctor, I
gave in to pressure to get vaccinated. On August 17th I received the Moderna
Vaccine and started feeling ill three days later. I never recovered, but
continued to get worse. I developed multisystem inflammation and multisystem
failure that medical professionals could not stop. My muscles disappeared as if
to disintegrate. I was in ICU for several weeks and stabbed with needles up to
24 times a day for those several weeks, while also receiving 6 or 7 IV’s at the
same time (continuously). It was constant torture that I cannot describe. I was
no longer treated as a human with feelings and a life. I was nothing more than a
Covid Vaccine human guinea pig, and the doctors were excited to participate in
my fascinating progression unto death. If you want to know more, please ask my
wife. I wished I would have never gotten vaccinated. If you are not vaccinated,
don’t do it unless you are ready to suffer and die!”

Mike did not deserve the pain and suffering he endured. He was a good man and
deserved better.

Michael’s full Obituary can be found here.
