Cutaneous Leukocytoclastic Vasculitis is an inflammation of the small blood
vessels in the skin throughout the entire body.

Bonnie is unable to walk and in serious pain due to severe Vasculitis from the
Pfizer Vaccine, she said the pain is so bad she cries every day from it. The
rash came out within 3-4 days after the 2nd shot.

Bonnie developed painful “red, blistering spots” all over her legs. The pain got
so bad that she is unable to walk and now is in a wheelchair.

The rash breaks out continually and blisters and burns, and some of the blisters
are the size of a golf ball. They believe the vasculitis has also affected her
bowel as Vasculitis does affect the whole body. She also now has severe
headaches and it has affected her speech.

The hospital has confirmed that the rash and her adverse reaction is due to the
Pfizer vaccine and the doctor also confirmed that he has others with the same
issues.

She now has homecare to help her shower and to help her around the house as she
cannot walk and has to rely on her carers and her family for everything,
including her toilet needs, as she is so disabled. She is presently in diapers.

Bonnie was warned by Public Health, NOT to share her story publicly, and they
still want her to get the booster shot!

Bonnie says she has been abandoned by the Government, and is not receiving any
compensation. She is currently in search of a lawyer and regrets ever taking the
vaccine. She shares her story here to warn others of the potential dangers, the
deception and nightmare she’s now living.

