Carther’s story told by his Mum, Shara Thacker-LeSarge:

Carther was still on the fence about getting the Vaccine. Then the announcements
started to trickle in. One university, then another... If you’re not FULLY
vaccinated, you CANNOT be on campus. He had NO CHOICE. To attend University that
WE (not the Government) pay for, he cannot choose. He was told, and he listened.

He jumped in the jeep, attended at Sperling Drive vaccine clinic in Barrie on
August 17th and received Pfizer. By August 19th, something felt off. He felt
different but couldn’t explain it. He didn’t complain. He sucked it up assuming
that most felt like this, or that it would pass.

He had flutters in his heart. He felt lightheaded. He had chest pains. He felt
off. He sucked it all up, until August 27th when he was rushed via ambulance to
the hospital and by August 29th, he was a patient in Mt Sinai.

Carther, my perfectly healthy, active, no medical history, no fat on his body –
Mr healthy, has been diagnosed with Pericarditis.

My son has a heart condition. My son has a team of cardiologists. My son is now
on heart medication for at least three months. My son cannot do anything that a
``normal'' 19-year-old can do. He cannot do Anything that raises his heart
rate. That includes walking more than a few minutes. Yes, walking. He can’t lift
anything. He is 19 in the body of a 99-year-old.

If he adds any stress to his heart the pericardium can scar. If that happens, he
will require surgery to remove the hardened sac around the heart. My son is in
constant pain. Excruciating pain. This is not pericarditis. This is pericarditis
by the MNRa vaccine.

Even the medical team at Mt Sinai is learning as we go. They don’t know the
long-term effects to the heart. They don’t know if he will relapse every
year. They are guessing and treating the best they know how.

These side effects are not listed on the piece of paper that you get when you go
for your vaccine. The nurses don’t tell you pericarditis is a possibility; and
hey, your 19... well in Male 18-23 year old’s you now have a higher risk of
heart complications. They discovered that in June. Nobody tells you this. Nobody
cares. Everyone thinks you’re stupid if you don’t get the vaccine, or you’re
selfish; or just uninformed.

If I could go back, I would. If I could tell Carther to not go... ignore the
university demanding you be a puppet, I would.

You have not sat with your child experiencing heart attacks over and over. Your
child doesn’t have a cardiologist because of the Covid vaccine. Your child
doesn’t need to go for cardiac echoes every week and ECGs every two weeks. Your
child isn’t struggling to breathe and in a constant 7-8 pain daily. Your child
doesn’t wake like they’re going through chemo treatments and is sick as hell
every single day from the heart medication and NSAIDs, until mid-afternoon.

My son’s life may never be the same. My son has lost so much because he
listened. He did what the Government said he had to do. I’m happy for you that
you don’t know what that feels like.

He is now exempt from Vaccine two obviously; Now they expect him to swab his
nose twice a week to attend campus as he’s only single-vaxed. No!!

Well to anyone who knows anything about Covid, the vaccines and how it all
works, guess what? I’m double vaxed... and I CAN get Covid. I CAN spread
Covid. I CAN carry Covid. I CAN die of Covid.

Do your research. If you have a son, friend or grandson who’s between 18-23,
hold off. I wish somebody had of told me. I’d do anything to go back!
