

Mariah telling her Mum’s story:

MY MOM’S WORST NIGHTMARE.

On April 6, 2021, Tiffany received the 1st dose of the Pfizer Vaccination with
no immediate concerns.

Twelve days later on April 18th, we were watching TV, when suddenly she turned
to me, visibly shaking, slow in her speech and nodded when I said I was calling
911.

She couldn’t form full sentences, couldn’t walk, had no motor function, couldn’t
hold a glass, didn’t know her last name or what year it was.

I remember that she then started crying, and telling me how much she loved me
and started to fade out. I was shaking her vigorously to keep her awake, when
the Paramedics arrived. Her BP was 70/30 and then, moments after, she became
coherent but was very delusional in speaking.

The Paramedics accused her of being on some sort of drugs due to her delusions.

THE DIAGNOSIS Within the next 15 days, there were 3 hospital admissions and
countless tests. My mom was given several diagnosis’ such as: Vasovagal Syncope,
POTS, Autonomic Dysfunction, Meniere’s Disease and Vertigo.

Many didn’t know what was wrong with her until eventually they said that it was a reaction to the Pfizer Covid-19 Vaccine.

My mom is still not fully released to drive or work. She has extreme fatigue,
all over muscle pain, tinnitus, blurred vision, vertigo, brain fog, memory loss
and several other symptoms every single day.

Three ambulance rides, four hospital visits, countless tests, doctor after
doctor.

Tiffany has shared, “Hopefully my story will bring forth much needed
awareness. I just want healing and to be able to connect with others who may
have had the same experience and are looking for support as well. Praying that
through my freedom to make my own health choices, I can heal from my injury.”
