Lyndsay Morton, Telling her Daughters Story, on 27 June 2021:

At 10am on 26th June my 19-year-old had her first vaccine. She leaves feeling
perfectly fine and we go shopping for the day, travelling home at 4pm she starts
feeling as if she has travel sickness

At 4:15 she collapses. We got her up, tried to walk her home and she collapses
again had to phone Dad to come and put her in his car, then drives her 2 minutes
home, gets out of the car and collapses in road outside her house. By now she
has pins and needles in arms and legs, pain in lower left lung and throat feels
tight. We call an ambulance who told us she needs to be seen quickly but they
are busy and I could probably get her there myself quicker.

At 5:30 we arrive at Whiston Hospital (Liverpool, UK) but couldn’t lift her out
the car and they wouldn’t get anyone to help, as nurses were too busy. We
struggle to get her in a wheel chair, get inside explain what 999 said and they
told us to wait in the waiting room with over 30 other people whilst she was
having convulsions in the chair with pain increasing in her lungs and leg.

Two hours later we are still sat with her in this condition so I decide to phone
a taxi to take us to the Royal Hospital. As the taxi pulls up, I tried to help
her out the wheel chair but she collapses again on the floor. Not one nurse came
to help, but other patients came over to help put her in the taxi.

8pm – we arrive at the Royal A\&E, I go in and ask for a wheel chair, they tell
me ‘if you can’t see any, there isn’t any’ I go back outside to my daughter in
the back of a taxi slumped over convulsing. The taxi driver went and found a
wheelchair outside and helped me get her into the hospital.

The triage nurse took her in within 5 minutes, as she’s pushing her in the
chair, she’s telling her she doesn’t believe she can’t walk and she’s not
reacting to it (the vaccine), as it hasn’t happened before. I’m told to leave
and someone will contact me in around 3 hours. A 19-year-old, terrified, but I
respect their policies and leave.

She’s left in the main reception room and then moved into a side ward as the
said they won’t want her to feel embarrassed shaking (to me at this point they
hide her away). She was left on this bed for five hours, alone, not improving,
cold, no blankets, no food, finally seeing a nurse to ask for painkillers as now
she’s developed a headache!

At 12:30 this morning, 8 hours after she first collapsed, she sees a doctor who
tells her it’s side effects (to the vaccine) that will last 1-2 days, and if
they last longer go back. She’s discharged and has to wait outside the royal
hospital alone at 1 in the morning on a Saturday night, weak and freezing until
we could get her! We have video’s that shows how she was left for 6 hours,
including her convulsions!

PLEASE THINK TWICE about letting your children have this vaccine!!

Brooklyn telling her own story:

“Unfortunately, I did have a reaction to the vaccine. Never did I think I would
be someone who would be affected by the vaccine, considering it has been
advertised in a such a positive light by our government.

This was one of the most terrifying things I have ever experienced in my
life. During the uncertainties of the outcome, questions ran through my head…
will this last forever? What is happening to me? Why is this happening to me? Am
I experiencing a blood clot or a fit?

While these questions circulated in my mind, I was in a room hidden from the
rest of the waiting room, because they thought I would be “too embarrassed” by
my convulsions. When in fact I was being hidden by the rest of the world by the
actual effects of the vaccine!

I debated getting it, by the unknown effects and also the stories that you see
from others about it.

I’m not someone to judge someone’s decision on getting this vaccine, but all I
want to do is make people aware and question whether this is the right thing to
do for themselves.

I’m 19 years old and I am perfectly healthy. I have no underlying medical
issues. So why would this affect me like this?”

