Carolina wrote the following on 9th November 2021:

After nearly seven months I am still dealing with side effects from both doses
of the Moderna Covid Vaccine which I received on March 17 and then June 17 2021.

Both have badly harmed my health. I was completely healthy prior to the
shots. Worked full time, farm work, rescued dogs, active, no health issues,
clean overall bill of health (except some neck/back pains here and there) and
seasonal allergies.

As of now I appear to have an unnamed mysterious disorder (variation of Gillian
Bare) or unnamed auto immune disease which causes overall nerve
inflammation. One week I have vestibular migraine. The other hemiplegic
migraine. and a multitude of other issues. The extreme inflammation (cytokine
storm blood work) affects my brain: how I think, how I speak, how I walk. It’s
slowed me down completely. I can’t even drive. It makes basic tasks hard to
understand, hard to accomplish.

Symptoms started like an allergic reaction within 30 minutes of the first jab
(along with expected side effects like arm pain, rash, fatigue, headaches). Had
extreme gastro issues, shortness of breath and Tachycardia following it. Then
the dizziness and brain fog, all took my energy. But I still wanted to be safe
from Covid and I took the second shot, as recommended by my PCP.

After the second jab I developed intermittent nerve pain (right side only) on
face, arm and leg plus dizziness. Symptoms worsened to include major pain, on
neck and back. Insane migraines that I didn’t know existed that it took me out
for hours and sometimes days. For 2 weeks I could only crawl to the couch and
not move. I have shocking pains all over my body. Tingling, numbness and burning
all over my skin.

So far, no effective treatment has been found for me. I have hopes this is
reversible , but it is unknown how better or worse I will get. Some days are
better, others worse. There is no clear trajectory of improvement. There are
good hours, good days and then horrible relapses.

I have been going to a huge number of doctors, specialists, blood tests, diets,
and more tests: PCP, Neuro, ENT, Cardio, Immunologist, and the list goes on. But
still no obvious answers or pathway for treatment.

I am trying hyperbaric chamber MHBOT, infrared lights, massages, multitude of
vitamins and supplements. Also, on new medication to control some of the obvious
symptoms (Hydroxycloroquine). I have also done MABs on Oct 13 and lots of
symptoms improved.

It is very hard not to be recognized by the medical community, whilst we were
trying to do our part and take our shot. Now we are pushed away from friends and
family members also. The struggle is real.
