I feel its important for people to know what I’ve been going through; it would
be irresponsible not to share.

I’m writing this sitting in the ICU with a foley catheter, IV’s, Oxygen, some
leg compression device and a ton of leads stuck to my body being monitored. I’ve
had multiple CT scans, multiple Ultrasounds, an Echocardiogram, a transfusion,
lab work done daily, and an MRV scheduled for today. I’m basically a human pin
cushion. I have blood clots in my leg and in both lungs, I’m short on breath and
am really tired, I can tell you that never in my life have I been so sick. At
one point I truly believed I wasn’t going to leave here upright.

There is a lot of pressure to get vaccinated for COVID, I waited because I
wasn’t completely comfortable with the vaccines yet, I simply wasn’t
ready. Well, I had to travel for a work event and as with everything else these
days being vaccinated I came to the realization that this isn’t going to end,
you can hold out but the roadblocks will only become more prominent. So, I gave
in, I set an appointment and walked in a healthy man and reluctantly got jabbed.

Roughly 8 days later I wound up in the emergency room. I was admitted last
Thursday and have been under close observation since. Doctors were confused as
my blood counts made no sense to them it’s a strange case as I’ve been told.

Well, here’s where it gets interesting, it turns out that everything I am going
through is a severe reaction to the Johnson \& Johnson COVID19 vaccine. That’s
right, this vaccine that is designed to save me actually put me in a
life-threatening position.

So, before you begin telling people that they’re “being selfish” for holding out
on the vaccine think long and hard on whether or not you’ve earned the right to
make that statement. There are very valid concerns that people have and I’m in
the hospital living through those concerns right now.

I am not anti-vaccine in general, I know vaccines can be a good thing. The
COVID19 vaccines had me concerned for multiple reasons and clearly, I’m still
not sold. I would never tell you to get or not to get the vaccine, it’s your
choice.

I pray nobody else has to go through what I have been going through, it’s
miserable. Before judging someone or calling them selfish please understand
there are real risks. Do what you feel is best for you and your family but do
not belittle someone else for doing what they feel is best for them.
