My name is Jessica. I am 33 years old, a wife, mother and a Nurse.

I wasn’t vaccinated until my company fell under the mandates, so then on 10/12 I
received my first dose of Moderna Vaccine. Some of the symptoms I had did not
show up for two weeks, but they were ringing in my ears, metallic taste in my
mouth, inflammation to my right eye, right sided weakness/tingling/numbness,
migraines.

I went to my PCP on 10/28 and received medications for migraines and was also
given steroids.

On 11/9, I opted to proceed with the 2nd Vaccine. I have two children and a
husband, whom I carry all of of benefits for.

My doctor did, and still does, believe this is absolutely Moderna Vaccine
related. This last vax however, has seriously wreaked havoc on my body. My blood
pressure has been sky high (wound up in the ER with stroke level BP) on
11/11/21. The diagnosis I received was “transitory HTN vaccination adverse
reaction.”

So now, I have two providers, my PCP and even the pharmacist at the pharmacy
where I received my vaccines, all telling me this is 100\% related to the
Moderna Vaccine.

Fast forward to after that ER trip, I have spent a week off and on in bed with
debilitating migraines. My BP and HR have both been extremely high. Prior to
this, my “normal” was 120/70 \& HR 70-80. Now, my systolic runs anywhere from
130-190 and diastolic 80-120. My heart rate can be 60 one second and in the very
next, 140. My BP cuff has an indicator which indicates my heart is out of rhythm
(this symbol only shows up when I am feeling “funny” or have a slight chest
pain). I have chest pain/tightness, shortness of breath, EXTREME brain
fog/fatigue, and honestly, just fatigue in general.

I just want to be able to be a wife and a Mama and I’m not able to be those
things to my family. I am working half days until I can get this sorted out. Oh
the irony….. take the shot to keep my job, yet here I am, unable to physically
hold out for longer than 4-6 hours a day. Before this, I worked 10-12 hour days.

This past Tuesday night, while watching a movie with my husband downstairs, (I
was reclining back), I told him I felt “funny” and had to sit up, asI felt like
I was slowly passing out while laying back. My heart rate was 140 and scared me
so bad that I did not even attempt to walk up the stairs to go to bed. I just
slept downstairs. I remember pre-vax, while working out, I couldn’t ever get my
heart rate over 120 no matter what I did! But now, all I have to do is sit
completely still. During these episodes I feel like I am going to pass out, but
I haven’t yet— fingers crossed. I am now monitoring my blood pressure numerous
times a day, have started on Metoprolol daily for the high blood pressure/heart
rate, have a cardiologist appointment next Tuesday (for a repeat EKG, echo,
stress test and holter monitor) and a follow up after that appointment with my
primary care physician.

I am so sorry for anyone else going through this. I am so sorry that I did what
I felt was best for my family. Looking back, I wouldn’t have ever gotten the
first one. A VAERS report has been filed, yet I haven’t seen anything from
it. I’m not crazy. You are not crazy. What we are experiencing is very real and
I won’t stop until someone hears us. If a patient is allergic and/or has an
adverse reaction to an antibiotic, are they called crazy? Are they shamed and
it’s “all in their head?” Nope. They are believed and they are heard… we will be
too!

Update…. today is day 10 post 2nd jab. Last night, I spent yet another night in
the ER as I thought I was having a heart attack and needed to be evaluated. EKG
this time showed sinus bradycardia. Negative D-dimer. CXR negative. All cardiac
enzymes within normal limits. Received a shot of Torodol for the chest pain with
no relief. Blood pressure looked okay. O2 sat dropping into the 80’s but would
immediately increase to normal limits without oxygen. ER Doctor, THE FIFTH
medical provider, acknowledged this is 1000\% Vaccine related and that it just
has to “wear off.” But how long?? How long does it take for this to “wear off?”

I am struggling mentally, physically and FINANCIALLY. Look at the medical bills
I am racking up, and we are only a little over a month into this!

But I won’t stop. I will not stop until I have answers. Until I have some kind
of treatment that will allow me to live a semi-normal life.

My husband and I were talking when I got home last night and in the TWELVE years
we have been together, we eventually decided I have only been evaluated in an ER
setting ONE time, and that was due to a miscarriage after a car accident. I do
not run to doctors every-time I sneeze. As a matter of fact, as a nurse, we are
the WORST patients, and much less to an ER. I have been evaluated by doctors
more in the last month and a half than I have in the last two years. Will it
ever stop???
