Debbie, who now requires bi-weekly Blood Transfusions, tells her story:

The week I took the Moderna Shot I knew something was wrong, but I thought it
was my weight that made my heart race and heavy breathing, but it was different
as I would take a few steps and it felt like I had just run miles.

The day that my husband took me to a doctor, my red blood count was at 5, 30
min. Later at the ER it was at 4, whereas the normal for women is 12-15. My body
stopped making red blood cells right after my first Moderna Vaccine on May 22nd
2021.

We are trying to use steroids to ‘jump-start’ my red blood cells. It was up a
point this week but it has been up a point before, only to drop. It requires 4
points more to be normal. I constantly feel like I will pass out, and there are
days that I just want to sleep. My body feels like it is suffocating or that I
will have a stroke from severe headaches such that I’ve never had before.

It’s now October and the Symptoms and Blood Transfusions continue. I knew my
numbers were down, but I was shocked at how low ( still only 5). The Dr tells
says he will do the 2 bags, then things go downhill from there. They take me to
the nurses that do the transfusions and it took an hour to get a vein. That’s
when I tell everyone to start praying harder, as I didn’t want them drilling
into a bone. With all of us praying that last jab, it worked! 3 loud prayers, 6
jabs, and an hour later I was ready, she said she hadn’t had to use 6 needles on
someone in years.

In Addition, I am forgetting how to say words. I could see myself spell out my
daughter’s name but for the life of me I could not say it….my daughter’s name!
And it’s like that with other words too.

Everyone should know the pros and cons. I researched before I got mine, but I
now know things were hidden. All I saw was how great it would be to not have to
wear a mask or not get Covid! Trust me, there are other horrors!

I don’t know your risk with Covid, so I’m not telling anyone not to get the
shot, but I am telling you that you are playing Russian Roulette. There are many
people like me that have major health issues from the Moderna Vaccine.

Now I have to get blood every 2 weeks. We won’t even talk about the medical
bills, for someone that doesn’t have insurance anymore.
