Mathilde’s Story in Her Own Words:

I received my first dose of Pzifer on Tuesday May 25th. On Wednesday evening and
Thursday I had purple left hand colour (left arm vaccine) and paralysis on this
side. I could not move my arm felt my arm hard and heavy.

The next day the arm pains are gone but my left leg started pain. The pain was
bearable but I was limping. Monday morning I get up and can’t put the heel down
anymore, it’s was super painful. I can’t move my toes they’re frozen.  I was
taken to Hospital and put on Morphine, Ketoprofen for a week but nothing
helps. I’ve been hospitalised for 10 days, during which I have lumbar and
medullar brain scan, then an EMG that confirms Radiculitis.

They Try to increase the doses of morphine and then corticosteroids but nothing
relieves me. I suffer from sitting, laying down, and standing limping – I have
no stability.

Coming out of hospital after receiving 5j of immunoglobulins + lumbar puncture.

I have had terrible side effects a week later at home: vomiting, bad headaches,
fatigue. I could not walk.

Again I was hospitalised a week later, to redo an EMG and immunoglobulin
treatment. I’ve had big blood losses (clots). Again we tried Acupan and
Tramadol… then a second EMG confirming that Radiculite is still present.

Today, 2 months after injection, I’m on anti-epileptic, neuroleptic, ketoprofen
and triptan 2 x a day because my headaches are so violent and hard to bear.

I have no recovery date since post vaccination Radiculitis is unknown.

I got vaccinated to secure a health and social post and today I’m stopping
work. I won’t be going anymore since my contract stops in 3 weeks. I’m angry and
disgusted!

La Presse de Gray have also reported on Mathilde’s case:

“When Mathilde Harismendy was on fixed-term contract, her manager “strongly
advised” her to get vaccinated to keep her job, which is what she did. As a
result, today, her daily life has become hell!

Gone are the days when Mathilde Harismendy could go shopping, walk or cycle with
her children around the lake. Go shopping with confidence or simply visit her
parents. Activities which seem harmless to many people, have become an ordeal
for the 27-year-old Frotéenne who has said goodbye, much against her will, to
her everyday actions since May, and now her job.”

