Within an hour of receiving the AstraZeneca Vaccine, I had extreme head pressure
and started developing neurological symptoms of burning and muscle pain along
with a quickened heart rate. I felt ill like I had a very odd flu for weeks with
a constant headache. I then developed severe rib and chest pain on week 3,
requiring an A\&E/ER visit.

They did an Xray and sent me home. The pain continued along with random leg
cramps and a breathless feeling. Six weeks after, I had an odd spell where I
almost fainted with an odd headache and more head pressure. My vision went funny
during that and I was fearful.

My eyesight was now diminished in one eye. I also started having strong pins and
needles in my feet and hands. My legs and arms also fell asleep often. Two
months and one week after, I had an anaphylactic reaction two days in a row
requiring hospital visits. A day after those I had atrial fibrillation. I was on
short term steroids and large quantities of antihistamines.

It was suspected by the hospital that I developed food allergies. I also showed
signs of unknown infection via my bloodwork and had developed type 2 Diabetes
(in January I did not have it). It was now mid May and I developed gland
swelling and tonsil issues. I began to lose my voice. I was consistently
frightened I would choke as even swallowing became tricky. I was eating a low
histamine diet and struggling to find food that didn’t make me start to have a
reaction. I also started reacting to everything around me and developing new
skin rashes and my hair started falling out. I then had odd mouth issues which
has been suggested as Burning Mouth Syndrome. I requested to see an ENT,
immunologist, neurologist, rheumatologist, anyone really who could help, but no
luck in doing so. Six and half months in, after seeing a dentist and multiple GP
calls, I saw an ENT who saw larynx problems and post nasal drip, but was
unconcerned about my issues as he felt they weren’t “sinister in nature”. Seven
months in, I paid to see a specialist that deals with Mast Cell Activation
Syndrome, which I have subsequently been diagnosed.

My life has changed drastically since the AstraZeneca Vaccine. I struggle to get
through every day, wondering if everything I eat, drink or breathe is going to
set off anaphylaxis.

I have struggled to get medical help since my Vaccine. I have felt ignored and
belittled. I have been treated poorly and as hysterical by an EMT, in my own
home, for having an Atrial Fibrillation attack. I have been ignored all night at
my hospital to wait in a dirty storage room while having an Anaphylactic
Reaction. The only actual care I’ve received is from a minority at my GP surgery
and my MCAS specialist. I have had many suggested temporary diagnosis’ since the
vaccine, including various types of Migraine, Neuropathy, Dysphagia,
Tonsillitis, etc. I have now been properly diagnosed with MCAS and Type 2
Diabetes.

I have reported my reaction to the UK Yellow Card Scheme, AstraZeneca, and of
course my GP and local Hospital are aware of what’s occurred. I have had a poor
response from AstraZeneca and none from the scheme.

It’s not right for the medical establishment to dismiss us, whether believed to
have been caused by the Vaccine or not, we still have a right to care. We are
being unkindly treated, gaslighted and our lives destroyed for doing so. We are
shunned as being anti-vaccine or being crazy because our bodies have not
responded as “normal”.
