I got my second Moderna shot and felt crappy for a week with fatigue etc. On
Sunday October 31st (8 days after vax) I felt like I might be getting a fever
and went to bed early. I was awoken with excruciating pain on my right arm,
upper spine, neck/shoulder radiating down my right arm.

All my muscles were twitching and spasming. My muscles in all these areas were
hard as rocks. I was unable to move without excruciating pain. I couldn’t get
comfortable no matter how hard I tried in any position.

Over the next two weeks I went to the ER four times and the walk-in clinic
twice.

It’s now almost three weeks later and the pain has barely subsided. I have been
on Morphine to even function, prescription strength muscle relaxers,
Nortriptyline for nerve pain relief and Torodol.

I am waiting for a MRI but they are so backed up and said it could be six months
to a year!

Luckily I met with a doctor who seemed very interested when I told her about the
Vaccine eight days prior. She took notes and didn’t brush my concerns under the
rug.

I found something online called Parsonage Turner Syndrome and one of the causes
is vaccination. My symptoms follow it to a tee. So she said she would treat it
as such. She marked my file as urgent because I was in tears from the
pain. Luckily they responded quickly and I am now meeting with a neurologist on
November 30th.

One of my previous co-workers contacted me and said he had the exact same thing
happen to him five days after the Moderna Vaccine and has been dealing with it
for seven months now, and no doctors will listen to him either.

Also, a man who comes into my work said the exact same thing happened to him as
well, following his second Pfizer shot.
