Anna telling her daughter Casey’s story:

This is just a small part of what my daughter of 23 is going through, caused by
one dose of the Pfizer Vaccine.

It’s now four weeks of this and getting worse, with the bad episodes, she also
loses the ability to talk! She’s in constant pain that is excruciating,
especially when she’s having a bad episode, which can last from half an hour or
for many hours at a time! her legs are either in agony or then numb. Her partner
said her pain was a 10/10 and he couldn’t even touch her legs without causing
her agony.

The pressure in her head is unbearable and getting worse with each
episode. She’s struggling to walk on her own and when walking over 100 metres it
sets off an episode. This has happened twice today whilst getting her into her
blood’s and doctor’s appointment, with no wheelchair available!

I wanted to film her today but not allowed to in the med lab. She was sent home
from the hospital with false information on her discharge papers and given meds
for anxiety and schizophrenia, suggesting someone in her family told them that
she has a history of tics, which is utter bullshit! It’s been written in her
release notes... the bastards! She did not have either of these before the
vaccination... what the hell are they thinking!!

Please, I continue to ask to pray for my girl, that we figure this out soon, and
that it stops getting worse each day!

My heart is just breaking for my girl.

Casey bravely tells her story below:

“I’m done being silent!

I’ve recently been dealing with horrible side effects of the vaccine. I have
ongoing muscle spasms and what the Doctors are referring as Tics. I get bad
episodes where my body convulses for ages. I can’t control the Tics. I also get
Vocal Tics, and all over Body Tics, and I can hardly walk now.

I can’t drive, nor work – which is why I got the vaccine, so I could work!! Now
a lot of things have been taken away. A lot of doors maybe closed for good.

The Doctors have admitted it is a bad reaction to the Pfizer Vaccine, and that
it has more than likely made any underlying issues worse. I’ve been dealing with
it a few weeks now, with no sign of it stopping.

I do not judge ‘Anyone’s Choice’. You can be anti-vax or stand with the vaccine
and I’ll still support you.

What has hurt me most of all is family members have treated my issue as if it is
nothing – trying to make themselves feel better. Because they believe in the
vaccine.

I want others to know the truth. I took the vaccine believing it will help and I
was wrong. Others have reacted badly also.

When I was rushed to the hospital unable to control the tics and unable to walk
or communicate (this bad episode lasted all day), I heard Doctors saying how
someone else had also been rushed in, unable to breathe because of a bad
reaction to the vaccine.

I do not want to change your opinion. I only want people to know my story and
what I’ve been through.

Casey”
