My partner had his second AstraZeneca vaccine on 6th July 2021. He was fit and
healthy beforehand and on no other medication.

He thought he had sickness and diarrhoea and came home from work on 16th July
. He still felt unwell on 17th and that night at roughly 23.30 he collapsed on
kitchen floor having a Tonic Clonic Seizure.

Ambulance was phoned and they took 2.5 hours to arrive. In that time he had
another 4 seizures. One of which was in bathroom where I noticed he did not
actually have diarrhoea, but was in fact passing Melania ( black blood).

He was taken to hospital alone due to Covid. I went up to the hospital four
hours later and was told he was bleeding from the stomach and had a bleed on the
brain.

He has become somewhat better, but after MRI scans, CT scans, Colonoscopy and
Endoscopy, two blood transfusions and given platelets, we have no answers and
medical staff are dismissive when asked could this be a reaction to the
Vaccination.

He has been left very unsteady on his feet and weakness in left arm and leg,
with a limp that appeared over night.

He has not had a stroke we have been told. He is on very high dose of Keppra
which makes him tired and very irritable.

He can’t work and is only receiving statutory sick pay. I am currently off work
to look after him.

It’s disgusting that they won’t give us a straight answer. I would never tell
anyone not to get vaccinated, but I’m angry that no one will admit when there is
a serious problem. How will they ever get proper statistics if they won’t even
acknowledge that people are left dead or disabled!!

