Steve had a severe reaction to the covid vaccine. 10 days after being vaccinated
on 24th May, he began to experience numbness and tingling in his legs and
feet. This resulted in his legs giving out, and him collapsing and experiencing
some pretty serious falls. He went straight to the ER, and hasn’t left the
hospital since.

He is now completely paralysed from the waist down, and has some paralysis in
his upper extremities as well which is gradually getting worse.

He started out in his local hospital where he had 9 treatments of Intravenous
Immune Globulin (IVIG) therapy, and they did not help. Things continued to get
worse.

He is now being treated at The Mayo Clinic in Phoenix. He has had 2 spinal taps,
multiple tests such as MRI, CT scans, nerve conduction tests, etc.

The news from these tests was not good. He is showing severe nerve damage, and
it continues to linger and cause further damage.

Steve has a team of the top neurologists in the nation working with him. After 2
long months, we finally have a diagnosis, we think. It is called Chronic
Inflammatory Demyelinating Polyneuropathy, a very aggressive form of Guillian
Barre Syndrome.

This disease is a neurological disorder that destroys the myelin sheath that
protects the nerves and nerve roots. It causes severe motor and sensory
disturbances, as well as paralysis.

On July 23rd, he had a port surgically placed, and has begun an invasive
procedure called Plasmapheresis. He will have one treatment each day for 5 days,
then more of the IVIG.

Steve and his family are praying the treatment(s) that that he is receiving
turns things around. The doctors believe that he will need IVIG treatments
indefinitely, and he has a very long and difficult road ahead

