Written by Jessica’s Family:

Jessica had been vehemently opposed to taking the vaccine, knowing she was in
good health and of a young age and thus not at risk for serious illness. In her
mind, the known and unknown risks of the unproven vaccine were more of a
threat. But, slowly, day by day, her freedom to choose was stripped away.

Her passion to be actively involved in her children’s education—which included
being a Room Mom—was, once again, blocked by government mandate. Ultimately,
those who closed doors and separated mothers from their children prevailed. It
cost Jessica her life.

It cost her children the loving embrace of their caring mother. And it cost her
husband the sacred love of his devoted wife. It cost God’s Kingdom on earth a
very special soul who was just making her love felt in the hearts of so many.

Surrounded by her loving family. Jessica was an exceptionally healthy and
vibrant 37-year-old young mother with no underlying health conditions.

Jessica’s greatest passion was to be the best mother possible for Bridget and
Clara. Nothing would stand in her way to be present in their lives. During the
last weeks of her life, however, the world turned dark with heavy-handed vaccine
mandates. Local and state governments were determined to strip away her right to
consult her wisdom and enjoy her freedom.

Along with being a superb mother, Jessica was a devoted and supportive wife and
created a beautiful, serene home for her family to thrive in while establishing
her family in the wonderful Laurelhurst and Assumption-St. Bridget communities
of Seattle. Jessica and Tom were a remarkable team who prioritized family values
and morals, and their Catholic Faith.

She was known best for her grace, wisdom, wit, sense of humor,
conscientiousness, her tireless work ethic, her pride in her family, and her
loving nature. Throughout her life she loved to travel and made many trips to
Europe, the Middle East, and Latin America, the Oregon Coast and Black Butte
Ranch yet she always valued who she was with more than where she was. In
personality Jessica was elegant and composed.

Within her altruistic regard for others, she held a special concern for the
welfare of mothers and children in need.

Left to cherish her memory are husband, Tom Wilson; her daughters, Bridget and
Clara; her parents, Arthur Berg and Gwen Berg; her sister, Elizabeth Berg; and
brother, John Berg; many extended family members, and a large friends group and
community.

