Charissa is a former EMT-Paramedic and Registered Cardiac Invasive Specialist
who has been medically diagnosed with an adverse reaction to the mRNA Covid
Vaccine(s). She had no prior history of blood disorders, but is now battling
severe anaemia, pulmonary embolism and micro-clotting, and needs 24/7 help
raising her four year old son.  Charissa Olivia Klamn

Charissa, in her own words:

I’ve been very sick. I was FINE before my Vaccine(s) and my blood work was
NORMAL

The Covid Vaccine(s) are officially the cause of my health problems, and my
blood transfusions. First it attacked my blood, requiring a blood transfusion
now my CK (Creatine Kinase) is sky high and my joints and muscles are literally
being attacked.

Multiple findings, so far it’s: Haemolytic Anaemia; Macrocyclic Anaemia; A
Pulmonary Embolism; Micro Clots; High CK (inflammation).

I see a specialist soon to plan the next steps, but these conditions are listed
under “rare side effects from the Covid Vaccine”.

I have been extremely weak and on home oxygen. I may need another transfusion.

I’ve been slowly getting worse and I’ve been put on steroids because my joints
and muscles are flared up and I’m in so much pain.

Because this is considered a severe adverse reaction I am going to seek legal
compensation, but right now I just need to get better.

I am now exempt from any further Covid Vaccines!

I have full confirmation it was the Moderna/Pfizer Vaccines and my doctor has
reported this to Health Canada. (Severe side effects from Covid Vaccine).

