Brittany suffered nine seizures in 24 hours, severe neurological trauma,
hospitalized five times in four weeks – all since having the Pfizer Vaccine.

Brittany received her first Pfizer injection on Monday August 9th, at a local
Walgreens. She developed dizziness and a severe headache while driving home. She
also felt numbness and tingling in her extremities, but dismissed it all as
normal side effects after the injections. So, we went to sleep thinking she’d
wake up feeling normal. That didn’t happen.

She had fully-body numbness in addition to severe headaches, tingling sensations
in her limbs, sharp pain behind her eyes, and confusion the next morning. She
went to the emergency room, was tested for COVID-19, and sent home. A nurse told
her, “there are too many COVID positive patients in here right now, we don’t
want to potentially expose you. Come back if symptoms worsen.”

She laid down for a nap when she got home and woke up two hours later to use the
bathroom. Next thing she knew, she woke up in the hospital. Her boyfriend found
her on the bathroom, unresponsive, in a pool of urine as she lost bladder
control. Paramedics took her back to St. Lucie Medical Center, the same place
that sent her home hours earlier.

Unable to speak, Doctors actually performed a CT scan this time. But they said
everything was normal despite her condition being anything but. She had no idea
what had happened to her or how she got to the hospital. Nurses kept coming into
the room, asking her questions. But she couldn’t speak, feeling trapped in her
own body. She was finally, after about an hour, able to blink to signal yes and
no and also used a writing pad and pen to communicate. She wrote the following:

“I know what I want to say, I can hear you, and understand you. Just can’t get
the words to come out. I don’t know what’s going on.”

Nurses conceded she “might” be having a reaction to the Pfizer injection. But
they still “strongly recommended” she go home because there are a lot of COVID
patients in the hospital. The next day, August 11th, after realizing St. Lucie
Medical Center was a worthless joke, Ms. Jouppi went to Cleveland Clinic
Traditional Hospital. Doctors performed a battery of tests – MRI, X-rays, EKGs,
ultrasounds, etc. It was the electroencephalogram (EEG) that revealed seizure
activity. Doctors prescribed anti-seizure meds.

Brittany Writes:

“This isn’t easy to share, I’ve made a promise to myself to spread awareness,
connect with others who are experiencing neurological issues post Vaccination.

I was admitted in the ER last night, I’ve had 9 seizures within these 24 hours
and am currently utilizing a walker to get around, with very shaky legs when
standing. Still in process of figuring things out. I have been discharged and
currently I’ll have in-home physical therapy 3x a week and a nerve study done
next week.”


