Riccardo was urgently hospitalised in Neurology because of the Guillain-Barré
Syndrome, 15 days after the Pfizer Vaccine. He was no longer feeling his legs
and unable to stand up and is hospitalised under observation with severe pain.

He had been vaccinated in order to continue working on the ambulances and avoid being swabbed every 48 hours.

Katia his mother says:

“My son had his first vaccination on September 28th 2021 for work reasons. Until
he was 17, I managed to keep him off the vaccine because I am afraid of it, but
then he turned 18 and was forced by his job to take it. He had very strong pain
in his legs just a few days later and, for this reason, we took him immediately
to the emergency room in Imperia. He has never had any of these symptoms before,
it all happened suddenly”

Riccardo was censored on Facebook but wrote: “Facebook is deleting it for me but
I’m reposting it…..  I’m forced to stay in bed and not be able to get up and
walk with my own legs like I did until 7 days ago…. full of pain…. Forced to
urinate like a fucking parrot in bed…. continuously have some crisis of pain….
For what? For a fucking vaccine they force on you to do your work….”

“Bloody bastards…. Forcing people to vaccinate themselves…”

“Making doctors and nurses lose their jobs, and many other people who don’t want
to vaccinate…. Shame on you!…..What if it was your son? Or a relative of yours
hospitalised in a serious condition?  What would you do?….

DON ‘ T VACCINATE!!!!!!!!!  GET JUSTICE……!!!!!!!!  DON ‘ T PROTEST FOR FOOTBALL
OR FUCKING PARTIES…..  PROTESTING FOR VACCINES, NOT TO VACCINATE ANYONE AND
GETTING THE FUCKING GREEN PASS……  WAKE UP!

