I’m telling my story in the hope of helping someone who may be experiencing the
same injuries that I did from the Moderna Covid-19 Vaccine.

When the vaccine was EUA approved I was very skeptical because I carry an
EpiPen. I waited for months because I just wasn’t comfortable. Family members
were telling me I needed it and I was just scared. Even though something didn’t
seem right to me, I decided to go ahead and take the vaccine because I am a
teacher.

I took my 1st dose of Moderna Vaccine on 21st May 2021. On the day after my
vaccine everything seemed fine. Two days later I developed a headache so severe
I could barely put my head on the pillow. I took Ibuprofen and felt better the
next morning. Later that week I became nauseous and was vomiting at work and I
developed a blistering rash on my back that hurt so bad I couldn’t touch it.

I visited my PCP and had tests run to figure out what was happening. After the
tests came back normal, I was told that I was experiencing side effects from the
Moderna Vaccine and they would fade as time passed. But to my surprise they got
worse.

About two weeks later, I ended up in the ER. I was in complete agony. My lymph
nodes were swollen in my neck, underarm, and groin. It felt like my entire left
side was numb and I needed assistance while walking. My blood pressure was near
stroke levels and my heart rate dropped below 40. My head felt like it was too
heavy for my neck. I could barely hold it up without having some support.

I had an EKG, DVT scan on my left side , Covid test, and several other
tests. Every test came back normal.

My final diagnosis was Myalgia resulting from the Covid Vaccine. I was told to
discuss with my PCP to determine if I should receive another dose. I have been
recommended not to receive any additional doses.

I went from working out weekly to almost no mobility. I’m thankful that I have
healed as much as I have, but still have to visit a neurologist and have an
upcoming visit with the cardiologist.

Six months later and I’m still experiencing numbness in my fingers and toes and
extreme exhaustion at times. My PCP says that the symptoms should eventually
fade.

The hardest part about this has been the lack of empathy from others who’ve not
been affected by the vaccine. I’ve been told that I shouldn’t talk about it or
tell others because I will discourage them from getting the vaccine.

If you have had bad effects you’re not alone. You’re not crazy. Keep the faith
and I pray that you recover well. I am still pro-vaccine but I hope that they
will try to figure out what the common denominator is among those of us with
these reactions so an improved vaccine can be developed.
