Admitted to hospital from 1st March 2021 until 4th April 2021

Written by Adrian 2nd November 2021:

After the AstraZeneca Vaccine I felt generally unwell but expected this, so I
just tried to carry on with life as normal, thinking that it would soon wear
off. On 28th February 2021 I felt really ill, my body ached all over and I had a
fever. I booked a Covid-19 PCR test for that day and my results came through the
next morning, Monday 1st March, as negative.

I was now getting severe chest pains and contacted my local GP surgery who told
me to go straight to hospital. I went to my local hospital in Grantham where
blood tests showed my platelet count was 7, so I was then transferred within
minutes to Lincoln County hospital, where scans revealed multiple blood clots. I
spent 34 days in Lincoln hospital and was fed through a tube because of a blood
clot in my portal vein from the bowel. A full removal of the bowel was
considered and, on the 8th March 2021, my wife was called to the hospital and
was told that I might not survive. Thankfully I did survive and I still have my
bowel. My haematologist told me that one of the main reasons that I survived was
because I was previously so fit and healthy and he said that the amount of
medication that was required to keep me alive would kill most people.

An account of how I was treated by the Medical Community: Initially doctors were
sceptical that it could be an adverse reaction to the AstraZeneca Vaccine, but
then came round to the idea, saying they had to investigate all other possible
causes before formally diagnosing me with Vaccine Induced Thrombosis
Thrombocytopenia. My Haematologist and the nursing staff were superb. My
Haematologist even rang me with some test results when he was on holiday.

I was on that many different forms of medication via a drip, that I was that
‘spaced-out’ for much of my time in hospital. I was not entirely sure of what
was going on but was merely trying to survive. I had a pick-line fitted, through
which they fed me. I was on extremely high doses of steroids, blood thinners and
I was given both blood and platelet transfusions.

When the nurse pushed me out through those hospital doors on the 4th April 2021
I breathed a huge sigh of relief that I had made it out of hospital and
survived, but that was only part of the battle won. To this day the battle
continues, and looks like it will for a very long time.

I am still on five lots of medication and have been told to expect to be on
blood thinners for the rest of my life.

A message to others about how this has impacted your life:

I was a very fit, healthy and active 47-year-old male, a non smoker who drank
very little alcohol, a sub-4-hour marathon runner and former semi-professional
football referee. Now I cannot even live independently as I am dependent on my
family just to live on a daily basis. I am breathless every day. Even getting
dressed leaves me breathless and I have to sit down to recover before I can do
anything else. I cannot walk normally, I shuffle along like an old man because
my legs are that weak that I cannot walk with a normal stride pattern.

I have had to purchase a mobility scooter to try to give me more
independence. Many days I do not bathe because I am too exhausted. I feel like I
just exist, but no longer live as my life as I knew it has been taken away from
me.

I am now being treated for chronic fatigue syndrome and waiting to see the
respiratory consultant at Lincoln Hospital.

Myself and my family have been affected physically, mentally and
financially. There is a real possibility that we could lose our home at some
point in the future as I have not been able to work since the 26th February 2021
and I am now at a point in my life where I am starting to think that I may never
be well enough to work again.

We cannot even go on a family day out because I cannot walk more than a couple
of hundred yards, some days I cannot even walk 50 yards. I am constantly
fatigued physically and mentally, life is debilitating and some days I wish that
I had not survived as I don’t want to live the rest of my life like this.

I did the “the right thing”. I had my AstraZeneca Covid-19 Vaccine and now
myself and my family have had our lives flipped upside down. The government
should be looking after people who have been severely adversely affected by the
Covid Vaccine’s so that we can live without worrying about how to pay our
mortgage and household bills.

I am not anti-vaccine, I did “the right thing” as directed, and have suffered
ever since!
