Eva tells her story:

My reaction was not immediate. I developed chills and numbness/tingling about 10
days after my second shot.

Shortly after, I developed worsening ear and head pressure. I initially
attributed all of this to a chronic sinus infection because I previously
experienced ear infections and allergies.

I then developed an incessant eyelid twitch, insane heart palpitations,
tachycardia, severe chest pain, and shortness of breath.

All of my symptoms persisted, so I finally saw my primary care doctor in May,
who ran standard blood tests, an EKG, and referred me to an ENT and
cardiologist. I was still at a loss.

Then the debilitating pain in my legs started. It was so excruciating that I
could not shower, stand, or walk. It spread to my upper body shortly after, and
was accompanied by nauseating head pressure that had me curled in the fetal
position for days.

I went to the ER when I realized I was losing my balance and sensations in both
legs. I feared paralysis.

After an MRI and CT ruled out MS, I was sent home to cope alone with the pain.

I continued to develop many new symptoms months after, with no answers or
treatment.

I was perfectly healthy prior to my second Pfizer dose, and I knew this was no
coincidence after all of my tests came back normal.

I don’t have a life anymore. My pain has reached a point that it is constant and
debilitating, so I can no longer do simple things like walk, clean, go to the
store, or take care of my son. I am at the mercy of my family.
