Antoine Méchin, a professional triathlete from France, suffered a pulmonary
embolism immediately after receiving the Moderna Vaccine.

He wrote:

“Sports season over, following lung embolism due to Covid-19 Vaccine – 1st dose
Moderna end of June 2021.

Two weeks later, while I’m in the Pyrenees for training with the compère at
Arnaud Guilloux, I’m starting to feel oppression.

I then take part in a trail on my way home and on this race, I feel I’m quickly
out of breath and a pain in my left arm, back and heart.

The following day July 18th, my doctor advises me to go for exams at the
hospital in Saintes. No worries detected, they tell me it’s definitely stress
related, and tiredness.

So, I’m off to the US to do the IM Lake Placid. When I don’t get too high
cardio, I don’t feel much and so the race goes well for me, without experiencing
any significant inconvenience.

After my sports break of a few days following the Ironman, I’m gradually
resuming on low intensities, I feel I’m not in good shape but no specific
pain. I then do my 2th dose of vaccine, so I can swim in the pool.

I feel like I’m bridged on high intensity efforts, sometimes I have discomfort
in my chest and back, but I don’t worry. I do Duathlon D1, knowing I’m bridged,
and the day after the race I feel this chest oppression more. I ride on Mondays
with @pacometl to show him our lovely Charente coast, and ended up solo with
5/10ths well pressed where I feel I have strength but there’s a concern at the
breath.

I’m talking to my doctor about the insistence of a sponsor friend
@jardinsdesaintonge who doesn’t find me well, and I’m heading to Bordeaux for a
cardiology appointment today. Explaining my symptoms, and @medical.stadium’s
ultra competent cardio explains the increasing number of post vaccine reaction
of this type and urgently spreads a scintigraphy.

I am now under treatment and hope to get back to my lung abilities in 3/6/9/12
months? Waiting for rest and low intensity for several months.

Sad reality, sad measure, sad government!
