So this message is for everybody out there that is posting their... bullying
posts about "you're an asshole for not being vaccinated", "you're the reason I
still have to wear a mask because you won't get vaccinated"... this is for you
guys.  I originally didn't want to be vaccinated, because there is no long term
stydies yet, and prior to march, on the 20/21, I was completly healthy, I worked
out with a personnal trainer twice a week, I had no health issues besides
migraines.

20 minutes after I've received my vaccination I returned to work and I said "my
god, I am so exhausted... can it really be that quick?" and they said "oh
absolutly", they told me to lay down for a little bit, and since that day in
march, my life really hasn't been the same.

Every single day, I have new symptoms. It is now august, and I am in hospital
getting an IIG, because I now have seizures. So, for all those people out there
that are sending all the bullying messages to the people that wanted to wait
because there are no long term studies on the vaccines, how about you quit being
an asshole? How about that? Because right now, some days I can't get up and
walk, my body hurts so bad, my joints hurt, my muscles ache, my vision changes,
and I haven't told a lot of people about it because, you know I don't want to be
one of those people that people look at and say "oh, she's an anti vaxxer"
because I'm not.

I just wanted to be safe, and I wanted to have a full story before I took the
vaccine, and I regret taking that vaccine.  I feel like my entire life changed
since march. I've, maybe had a couple weeks of normal days since march. So for
you people that are waiting, and feel like you're being byllied every single
day: stand strong and hold true what you believe, what you wanna do. It's your
body. And if you don't feel right about getting it because you're waiting for
the long term studies, then do it.

Don't do it, don't be bullied if you don't feel right about it. You need to do
what you feel is right.

