Theresa’s Story in her own words:

I had signed up for the Vaccine and was on a waitlist. While on the waitlist me
and my husband got Covid. We were pretty sick but not hospitalized. It was just
like the flu but on steroids. After that I felt safe from getting Covid again
and didn’t plan to get the Vaccine until I no longer had antibodies because that
makes LOGICAL sense. It took about 6 to 8 weeks to lose the brain fog.

Then societal pressure began to build and people began attacking the
“unvaccinated” and calling them anti-vaxers. The media and the current
administration are in overdrive with shaming and guilting. My daughter said I
couldn’t see my grand-babies until I was fully vaccinated because the CDC
recommends all people get vaccinated. However, in their wording they say the
Vaccine MAY be beneficial if you already had Covid.

I got my 1st dose of Pfizer on July 22nd, 2021 at 1:30 pm. I waited 90 days
after I had Covid.

A couple hours after the shot I began feeling sick. I was short of breath; my
throat was feeling a little tight and my chest felt tight too. As the hours went
on, I began feeling tired and thought this is all normal.

Around 9/9:30Ppm I felt a pain in my right calve. I also had tingling in my
hands and feet. I was concerned but told myself it can’t be related. No way
because I am reassured by all of the TV doctors, the CDC and the health
department the Vaccine is very safe. I went to bed hoping I would wake up.

July 23rd I did wake up but very sick. I was achy, had a bad headache, runny
nose, the chills, low grade fever, still shortness of breath, chest tightness,
throat was still tight, my skin was sensitive to the touch, nausea, diarrhoea,
coughing and racing heartbeat.

As the day went on my fever went up to 102.3. Around 9:30pm my hands felt cold
and finger felt numb and all of my fingers from the 2nd knuckle up turned
completely white. I knew that wasn’t normal. But they did get their color back
after a while. I felt like I had Covid all over but with odd symptoms. I
couldn’t even walk 20 steps without being short of breath.

July 24th, I began to feel better but still had a headache, fatigue, Loose
stools, tingling in extremities, coughing, shortness of breath. I scheduled an
appointment to see my family doctor the next day.

July 25th still had headaches, loose stools, coughing and shortness of breath. I
saw my doctor and she told me I had an anaphylactic reaction. She said I SHOULD
NOT take the 2nd dose because I could very likely die from the anaphylaxis
because the 2nd dose was much more powerful. She also said my immune system must
be strong which is why my body fought itself against the vaccine. Which is why I
am now wondering WHY we are being told we NEED the Vaccine if my body recognised
it already.

July 26th, I had coughing, shortness of breath and I began having strange
episodes of confusion, loss of balance, a pain behind my right eye, dizziness,
blurred vision, I felt like I was in a dream like an out of body experience. I
was unable to understand what the people on TV were saying and couldn’t
understand words were on the screen. I knew they were words but I couldn’t make
sense of them.

I saw a neurologist and after going through my medical history I was diagnosed
with having Mini Strokes due to small blood clots caused by the Vaccine.

I am a healthy 54-year-old, I am in shape, exercise daily, I eat right, don’t
drink, don’t smoke, I’m not on any hormones, I have excellent blood pressure and
cholesterol and I am 5’4 and weigh 123lbs. There is no other explanation for
this.

I have met so many people after sharing my experience who have had bad
reactions. A friend of mine lost her father within a week of getting his second
dose and another friend lost a family member within 2 days of the 2nd dose.

The neurologist told me she sees new patients EVERY WEEK that have neurological
problems, strokes, tremors, seizure and even partial paralysis after being
vaccinated.

I still suffer from short term memory loss and brain fog. I am still on blood
thinners to avoid future strokes.

Following the vaccine I have major mood swings and hot flashes even though I
passed menopause over a year ago. I also have periodic headaches that I never
had a problem with before and my nose continues to be runny.

THIS is WHY we SHOULD NOT mandate Vaccines

