Patricia’s Story being Told by her Daughter Michael Sutton:

My mother fell ill on 16th June from the 2nd Covid vaccine dose that she had
received on 9th June. At first we thought she just had a little bug but then it
quickly got to a point where she could not walk she was in extreme pain. She
cried consistently, she couldn’t feed herself, she could not use the bathroom by
herself and we had to help her all the time.

On 18th June we were feeding my mother when I decided to take her
temperature. Her temperature turned out to be 102.9. That is when we decided to
call the ambulance. Once she got to the hospital they quarantined her and gave
her a Covid test but could not figure out exactly what was wrong with her. It
literally took a week or two for them to figure out her diagnosis.

This shot gave her a condition called polyneuropathy aka chronic
pain. Neuromuscular weakness, hypertension, hyperlipidemia, peripheral
neuropathy, functional debility, insulin dependent Type 2 diabetes and
generalized weakness. I know that’s a lot to understand, so pretty much she was
not able to walk, she couldn’t lift her arms, she can’t grab anything, she
couldn’t Feed herself or wiggle her toes. I literally watched my mother go from
being healthy active and fun loving to a “vegetable”, laying in a hospital bed
crying in extreme agony.

As her child I could not believe it. I thought I was losing my mother I did not
know what to do. We try to reach out to the news station and they refused to
take the story because the president is putting so much emphasis on getting the
vaccine shot and how good it is for you, that they don’t want to publish any bad
stories.

We also reached out to Pfizer, that’s whom she got the shot from, but they are
also not helping.

