John’s Story Told by His Wife Susanne:

On the 5th March John got his first dose of the AstraZeneca vaccine. John was
glad to get it as he was so scared of catching Covid, which was down to the
media. All that we saw on TV was people dying and John was convinced he would
die if he caught Covid with his asthma. He was very paranoid like most of
Britain.

I was always against getting the Jab but John convinced me to get it when our
letters came. What was the chances of us both to go on the same day, minutes
apart, to protect my elderly parents as they had both had their two Vaccines.

I had a sore arm for 4 weeks, and a bit unwell for a day or two, but John seemed
fine after his until a week later when he started getting a sore head – that was
the start of him getting ill.

His initial symptoms were foggy brain, forgetful, not remembering lyrics to
songs he’s known forever, stumbling, no concentration, he thought he was getting
dementia and he was very scared.

John worked away and with the Covid situation he never seemed to be able to get
a doctors appointment. Jump 7 weeks ahead and John started having seizures. Then
got a phone call to say John was in Dumfries Royal in an induced coma and fully
ventilated!

Myself and our two oldest kids went there, where he was in ICU, and twice in 11
days we were told to prepare for the worst.

He was moved to the Royal Infirmary on the 17th May ,still having nonstop
seizures 24 hours a day. John’s seizures stopped on the 30th May. He was still
on 4 heavy duty sedations the whole time. Doctors tried many many treatments and
they called what John had ‘autoimmune encephalitis’, which causes seizures, and
never-ending epileptic fits.

All the doctor’s investigations came back with nothing. No cause could be found
and no reason for this to happen. A yellow card was sent away. For those who
don’t know what a yellow card is, it’s sent away to the UK Government MHRA to
report Vaccine Adverse Reactions – in John’s case to the AstraZeneca Vaccine.

Who’s left to pick up the pieces? Just us, John and his family!

John has a long way to go. He didn’t ask for this as he thought the vaccine
would protect him, but instead it nearly killed him.

WHY ARE THERE NO REPORTS ABOUT SERIOUS ADVERSE REACTIONS? NOT IN THE MEDIA OR IN
THE PAPERS? I AM NOT ANTI-VAX AS I GOT MY FIRST DOSE – I AM ANTI-LIES!

John’s life has been changed. Who is going to be held responsible when the
Vaccines go wrong as in Johns case?  ARE we supposed to just accept he was
unlucky? How many unlucky people are there who go un-reported and that we hear
nothing about?

It’s a crime!

I am so angry with this f****d-up Government and I am so f****g done listening
about how good these Vaccines are!

