56 year old Alex, lost his leg after he developed blood clots two weeks after
receiving the AstraZeneca Vaccine. He received his first dose on March 20th 2021
and was hospitalised on April 4th after collapsing at home. He developed blood
clots so severe that doctors had no other option but to amputate his left leg
above the knee.

Twelve days after the vaccine Alex complained of sore calves, “but I didn’t
think much of it” he said. The pain continued over the next few days and on
April 4th, Alex collapsed at home. “One minute I was doing the ironing and the
next moment my legs buckled from under me.” Alex was taken to hospital where a
CT scan confirmed multiple blood clots in his lower abdomen and in both
legs. Surgeons removed the abdomen clots which thankfully hadn’t moved into his
liver and kidneys.

“I had the vaccine because I want things to go back to normal as soon as they
can, and I thought the only way we can do this is by being vaccinated. I
wouldn’t want to discourage people from having the Covid jab, but from what they
know, what happened to me is rare.

“It has been quite a surreal few weeks. I’ve experienced the most horrific days
of my life but I’m still here and just need to keep fighting and keep being
positive. That’s all I can do.”

“I asked if they could amputate below the knee, just so that there were more
options when it came to getting mobile again,” said Alex. “But unfortunately it
had to be above. Every vein in my left leg was collapsing.

Alex was advised it could take up to a year for him to be fully mobile again,
with the help of a prosthetic leg.

“It has given me a whole different perspective,” Alex said. “It has changed my
life. I’ve lost my leg and my livelihood. I won’t be able to do scaffolding
again and there will be challenges ahead but I believe it will change things in
a positive way. Before all this happened I loved nothing more than dancing to
Northern Soul. I’m a terrible dancer so it’s no great loss – but I will dance
again?”

“I consider myself very lucky. I have family and friends, support and love – and
a whole lot of determination. It’s important to be thankful for what you’ve got
– and to remember there is always someone worse off than you.”

No More Silence have been in close contact with six other amputee’s in the
United Kingdom, all directly relating to the AstraZeneca Vaccine.
