Tayla telling her story on 05/11/21:

On the 25th of August 2021 I got the Pfizer Covid-19 Vaccine so that I could
keep my job in Nursing.

Two weeks later my resting heart rate went from 60 to 100bpm. Two weeks after
that I had a severe infection of tonsillitis at a grade 3-4 (pus, ulcers and
bleeding tonsils). This was a really quick onset as it came on within 3 hours.

First hospital trip I was just sent home with antibiotics and told that within
48 hours my heart rate should come back down to normal. Within 48 hours my heart
rate was still high so we made another trip to a different hospital, where they
told me I was dehydrated so they hydrated me orally and gave me a fast-acting
steroid and sent me on my way with the words “Your heart rate will come back
down in a couple of days”. I even got told that it’s normal for a 22-year-old
girl to have a resting heart rate at 110 even though I knew it wasn’t normal for
me.

Two days later I made an appointment with my doctor where she did an ECG and
also put a halter heart monitor on me for 24 hours. The monitor showed that I
had a resting heart rate at about 110-130. She sent me a referral to get an echo
done, which I couldn’t get for a week after that. During the time of waiting to
get my echo done I had finished my antibiotics, but then my ear piercings which
I’d had for a year now started to flare up with pus. Another trip to the
hospital where I waited in the waiting room with 5 other people that had chest
tightness, breathlessness and high heart rates – they were all around my age
20’s-30’s and they all just previously had their Covid-19 Vaccine!

I waited from 7:30pm till 2am in the morning to see a doctor. Mind you all this
time I still have symptoms of chest tightness, breathlessness, high bp, high
heart rate and a feeling of dizziness when I stand. By the time I saw a doctor
they did a chest X-ray and took some bloods but came to the conclusion that it
was just all anxiety. They gave me a diazepam and sent me on my way. That was on
the 5th of October and it is now the 6th of November.

After being dismissed and pushed to the side by multiple doctors and
specialists, to this day they still can’t find anything to diagnose me with. I
even had a doctor tell me there were no more tests that they could do even
though I had only had a couple of blood tests done, an echo and a halter monitor
on.

I haven’t been at work for 6 weeks now and I got the Covid-19 Vaccine so that I
wouldn’t lose my job, but now here I am not working, with no money, because of
the side effects of the Vaccine. It continues to frustrate me that no one
believes that there are people out there with adverse reactions to the
vaccine. I still haven’t been diagnosed with anything but I still have chest
tightness, breathlessness and a resting heart rate of 110. Before the vaccine I
went to the gym 5 times a week and maintained a healthy cardiac status. I
haven’t been myself since. My mental health has declined drastically and my
faith in the health care system has too.

When there is a risk of a medical procedure it should always be a choice, no
matter what. The only reason I write this today is to spread more awareness and
hope that no one else has to go through what I am going through.

For anyone who is going through the same as me, you aren’t alone, as there are
hundreds/thousands of other people out there exactly like us. We are always
taught in nursing about a person’s quality of life and right now I can say that
I have no quality of life, trying to live like this.

I won’t be silenced anymore.
