Tania telling her daughters story on 18th November 2021:

My daughter Faith is 16 years old and 12 weeks ago she had her 2nd Pfizer
Jab. As she works after school at a pharmacy, we thought she definitely needed
it asap. But 4 days after the jab she started to experience huge abdominal pain
and nausea. On day 6 after the jab we took her to hospital and I did ask ‘could
this be the vaccine?’ ….and was looked at like I was an idiot.

All her test came back normal but they were stumped, so they decided to take out
her appendix and explore around! Why they did it? Who knows, as everything was
fine even the appendix!

By this stage Faith had no appetite and just keeping her hydrated was an issue,
but she came home and she still had doubling over abdominal pain, although we
put it down to post surgery (we did not know at this stage that the appendix was
fine). Over the next few weeks she had pain, nausea and light/noise sensitivity
and was constantly itchy.

Around 4 weeks ago Faith seemed to really go downhill fast. She now has insomnia
and sleeps about 3 hours a night. Her pain got worse, she couldn’t eat and was
very sick. I took her to the ED and waited 11.5 hours and they did more test and
stated it was all normal, so they sent her home at 10pm with 2 prescriptions for
pain relief and sleeping tablets.

The week before this Faith’s paediatrician referred her to an immunologist who
said to us both verbally that it was indeed the Pfizer Vaccine that had
triggered it all, and she could be like this for weeks or months, but then when
he sent a report to the doctors and ourselves he change his diagnosis and said
it wasn’t the vaccine and that it might be post viral!!!

The next day she was worse again so I phoned Telehealth and they said to take
her to hospital immediately, which we did, and after many hours in the waiting
room with a drip they admitted her to the kids ward. That night everything
changed. Faith had a really bad 45 minute Tic as they call it, but her body was
thrashed around, her neck was pulling back and forth and her legs were also
slashing around. It was now 2:30am and the poor young registrar looked in horror
stating she had never seen anything like this before and was crying watching
her. They gave her some Valium and it slowly settled the main Tic, but from that
point on Faith started having short Tic’s similar to a Tourette’s
patient’s. They changed her medications and after a couple of days we went home.

When we got home it became very obvious that the night-time Tic’s would last
around half an hour, most nights. They are painful for her as all her muscles
are pulled tight and very sore. She has trouble with Tic’s during the day also
and eating, sleeping, light \& sound sensitivity and abdominal pain still. So we
went back to the hospital for another 4.5 hours in ED but they wouldn’t even
give her Panadol. We got taken into a little room with a paediatrician and 2
registrar’s and they pointed out how positive it was that it was “nothing
serious “ was wrong because all the tests were clear, BUT, he stated that
Faith’s problem was too much screen time!!! And that we could go home and lay
off the devices…..I was shocked to say the least!!!

Faith has been home for this whole time with no school, no work and no army
cadets ( last year she was cadet of the year). Faith wanted to join the armed
forces when she left school and we have been told that is impossible now.

We went back to our family doctor and he is arranging for her to go to the Royal
Melbourne Childrens Hospital so we can get some answers. She has not had an MRI
or seen a Neurologist and we are doing this without any help for the hospital.

Faith has now started ‘blacking-out’ over the last few days and the Tic’s are
worse ( I have footage).

We are all living an absolute nightmare at the moment and nobody cares!

The number of people damaged by these Vaccine’s grows each day, and everyone is
ignoring what is actually going on. I’m not an anti-vaxer, obviously, as we are
fully vaccinated, but these victims need help now!
