My name is Chantal. I’m a 37-year-old Police Officer from Western Australia and
I had a severe reaction after receiving the Pfizer vaccine.

In August, my employer announced that anyone who was not vaccinated against
COVID would be treated differently by having to wear masks at all times in the
workplace and excluded from buildings. This included being moved out of
positions that they have worked hard for into office type roles, if they are not
vaccinated (all confirmed by an industrial relations staff member). This
announcement is no secret to the community as it was published on the front page
of the West Australian newspaper.

Prior to this announcement, I had decided that I was not getting the vaccine. I
am entitled to my choice. Please note that I am not an anti-vaxer as some may
call it, but I make decisions based around having sufficient information
available to me which I believed and still believe I do not have.

Within 10 minutes of getting the Pfizer vaccine, I got vertigo and nausea and
within 15 minutes I had hives all over me. The doctor and ambulance officer got
the rash under control but as soon as I got home, I had a fever, chills and felt
very unwell. For the following three and a half weeks I suffered rashes every
day, fevers as high as 39.7, aching muscles, flu like symptoms, nausea,
vomiting, diarrhoea, pressure in my sinuses and a cough so bad that it felt like
my blood vessels were going to explode in my face. Some days I cried because I
thought I was going to die. I was so sick. When I thought I was starting to get
better, but still had extreme fatigue and was constantly light headed, I went
back to work, but spent a lot of time laying on my office floor and struggling
to get through the day.

On a Tuesday night, I noticed that my eyes felt weird. They had a heavy feeling
and felt like they needed rubbing all the time. The next morning, I woke up to
go to work and one eye wouldn’t open and the other wouldn’t close. The one that
wouldn’t close also wouldn’t blink. I thought that I had allergies so I took an
antihistamine and drove one hour to work. By 9:00am, I felt my top lip go a bit
funny and my work colleague told me that my face was drooping sideways and she
was taking me to emergency. I will be forever grateful for her making me go as
she saved my life. Within 1 minute of being at emergency, everyone was rushing
around me and I started to panic. Next second I’m getting wired up to machines
and a stroke specialist and multiple other doctors and nurses were in my
cubicle. I was admitted to the hospital.

The next morning, I got up and had a shower but I ended up having a stroke. I
was in the shower by myself and my body started waving uncontrollably and the
right side of my body got a weird sensation. I could no longer stand and I was
on the floor scared. My right side got really heavy and felt numb with a weird
pins and needles type of sensation. At this stage the left side of my face was
fully paralysed and I had extreme muscle weakness in my left arm and leg.

I was taken for more tests which showed that the main artery to my brain had a
rupture and I had suffered a mini stroke (TIA). I was transferred to the stroke
ward at a different hospital that day and from that moment on, I was monitored
hourly.

I can’t tell you how scary it was being in a stroke ward with all elderly
patients, thinking what the hell am I doing here. I was tested for every illness
and nutrient deficiency that could cause a stroke and the doctor said I was
perfectly healthy and had no possible cause to what had happened to me.

While in hospital, I was monitored hourly. It was crazy. No sleep, and I was
constantly scared that it would happen again. I couldn’t eat or drink properly
and dribbled everything down the side of my face. It was humiliating. This was a
minor issue for the doctors but for a 37-year-old girl, it was a big deal. I was
told that there was a 25\% chance it wouldn’t heal and if it did, it would take
months. This by itself was highly distressing.

I cried multiple times a day. It was mentally hard to get through every
moment. I was not allowed to move at first but the nurses let me have bathroom
privileges because going to the bathroom in a tray was too upsetting for me. If
I moved too much or too fast I could have another stroke. I was unable to have
any treatment as the doctors deemed it too unsafe so the only thing that the
doctors and I could do was wait and hope that my artery will heal itself. This
will take a long time and in the meantime, my usual activities are on hold.

When I was discharged from the hospital, I was really happy as I couldn’t stand
being locked up in the hospital. Don’t get me wrong, my nurses and doctors were
amazing and I can’t say one thing wrong about their efforts and caring
nature. However, it was so scary being home without the constant care. I wasn’t
allowed to be left alone and the risk of having another stroke was and still is
very high. I was in constant fear and even though my confidence is increasing, I
still worry every second. I am further away from instant care and the risk of
permanent brain damage is very real. I now also suffer constant nose bleeds and
painful joints.

I was booked in for an appointment at the vaccine safety clinic. Sadly, there
were about twenty other women the same age as me sitting around waiting. I
didn’t really understand what the appointment was about until I was taken into a
private room with a doctor who tried to tell me that the Pfizer Vaccine had
nothing to do with what had happened to me, but then also couldn’t tell me that
it didn’t. He sat in his chair stating that it was worth the risk of having
another stroke to get my second Pfizer shot. How can a doctor sit there and tell
someone those things. He was willing to risk my life to meet what I believe his
goal to be of getting as many people vaccinated as possible. He didn’t care
about my safety and even asked, after I refused the vaccine, if I wanted him to
call me back in three months time to see if I changed my mind. There was no
respect for my decision.

The mental side of this is very hard and has required a lot of strength. I am a
very active and busy person and to go from that to only being aloud to walk
around the house is highly distressing. I have to be very aware of my mental
health and I can’t thank my partner and friends enough for dropping everything
to help and support me. I am very lucky.

I don’t want anything from telling my story accept the acknowledgement that no
vaccine or medical procedure is safe for everyone. This is not my opinion; this
is fact, and the COVID vaccine is no exception. No one has the right to tell
someone else that they have to put something in their body, as they don’t know
the risks to that person. It is causing a sad division in our society and not
making anyone happy. If you choose to have the vaccine then great and if you
don’t then that is ok too. Please be kind to each other and treat each other
fairly and equally, we all deserve it.

The photo was me in hospital showing left side facial paralysis. Despite doing
everything the doctors told me, I’m back in hospital with a Gall Bladder
infection. They need to remove my Gall Bladder but can’t at the moment because
of everything else that is going on. I’ve been in extreme pain and was vomiting
blood. I’m on IV antibiotics every 8 hours.

To all the people who have told me that my experience isn’t real and that this
could never be true. Before you tell anyone that they are a liar or voice your
opinion, ask yourself two things – firstly, do I have all the information to
voice my opinion and challenge the experience of another and secondly, am I
qualified in voicing this opinion.
