Maddie telling her Mothers story:

My mother Wendy developed swelling in her knee 5 days post first dose of the
AstraZeneca Vaccine. Mum complained of severe headaches nearly every day post
vaccination.

A few weeks later her local Doctor sent her for a scan on her knee as she was
having trouble with it. She was sent to Bega Radiologist where they did a normal
scan to see what was wrong with her knee, but they did not do the correct scans
in order to identify whether the sudden swelling was due to a blood clot. My mum
continued in pain for 52 days.

On the 15/08/2021 my 15-year-old niece went outside to find my mother on the
ground and was unable to wake her up. She called 000 and then the ambulance
rushed Mum to Bombala hospital where she was later flown to Canberra hospital.

Later that night the Doctors from Canberra phoned my bother to tell him we
needed to apply for an exemption to cross the border as Mum had a life ending
Brain Haemorrhage.

The Doctors did everything they could to help us cross the border and to enter
the hospital as we needed approval to enter the ICU. Once we arrived, they
explained to us that Mum had had a Subarachnoid Haemorrhage and that she was on
life support and could pass at any moment.

Everything was a rush, from being put through 2 at a time with Mum, to being
asked about whether or not Mum was an organ donor. We didn’t have time to let
anything they were saying sink in.

Within the first 2 hrs we had the end-of-life specialist asking us if we agreed
for Mum to be an organ donor. We agreed as Mum was always the first person there
to help someone in need even if it meant she went without.

I asked the Doctors if this was caused from the AstraZeneca Vaccine and they
said no, because at this stage there wasn’t enough evidence to say that brain
haemorrhages were linked to the vaccine, but if more evidence was to come about
it then yes, they would link it .

I asked for an autopsy, but they went on to say that no autopsy would be done as
they know the cause of death and it wouldn’t show anything different.

Still to this day they deny it’s linked.

When we received Mums’ death certificate it states that Mum had passed from two
different types of brain haemorrhages – a subarachnoid haemorrhage and an
intracranial haemorrhage. The Doctors at the hospital did not mention the
intracranial haemorrhage to us at all!!

I put Mum on the TGA site but they have not linked Mum due to lack of physical
evidence. The lady from TGA has highly recommended that I put in formal
complaints against the Doctors and Radiologist as they should have done the
correct scans since Mum had swelling in her knee and an autopsy should have been
done.

I strongly believe my mother’s death is because the AstraZeneca Vaccine.

My mother was truly amazing. Mum was always there for us when we needed
her. Without my Mother here, my world is so much darker! She leaves behind 3
children and 7 grandchildren. Mum was the only grandparent my children have and
the only grandparent my nieces have.

Because of this Vaccine our children are now growing up without their Nan. RIP
MUM / NANNY We all love you and miss you more than you could ever know.

