I am a Covid PCU nurse. I volunteered to work the ICU/PCU July 2020, and
continue to treat Covid patients now. I wanted the Vaccine. I believed it would
end this.

The first dose made me very sick and fatigued. At first it was some heart rate
increase and facial flushing that I ignored. Then I spent Christmas Eve feeling
like I was hit by a train. It took five days of feeling run down and aches and
pains until I felt better. From that point on I had joint pain more than I had
before.

The second dose made my face feel numb and tingly. I did get this same feeling
with my migraines occasionally. That day I Face-Timed with my mother who’s also
a nurse. She was convinced I had Bell’s Palsy. I dismissed her.

Two days later these symptoms came back with a vengeance and never went away. I
started getting electric shocks in my left temple radiating behind my eye. I
would get headaches that would not go away with any treatment. I took pain
medicine that was OTC or prescribed and it wouldn’t touch it. The burning in my
face was insane.

My symptoms kept snowballing. I went to the ER for treatment and was told I
probably had shingles in my eye. Lol!

I Went to an eye doctor who quickly dismissed that and said no you have
Trigeminal Neuralgia. I had to wait for an appointment. My first appointment I
was prescribed Topamax and Gabapentin.

A MRI was scheduled. The meds were not good for me. Topamax knocked me for a
loop! The MRI discovered Intracranial Hypertension. Whoa!!! Where’d that come
from??? I was scared!

While waiting to see the neurologist the Gabapentin caused a kidney infection
and made me extremely ill. My symptoms got so bad with being dizzy, nauseous and
blurry vision I had to take FMLA that extended 3 months.

Since seeing the neurologist I’ve been put on Diamox that has been increased to
1000 mg, Lasix, several migraine meds. Although I can function better than when
I had to take FMLA,

I still have constant headaches, funky vision and sometimes fuzzy cognition. I
am waiting to see a new Neurologist to try for better treatment and hopefully a
better outlook.

I want something closer to my old life back.

