Nichola tells her story on Oct 28 2021: 

“So this is me yesterday at Alfred Hospital, after 8 days of feeling really
crappy and having given in to the pressure of getting vaccinated. Having an ECG
on my heart and waiting for a chest X-ray and Bloods to be taken. and possible
further screening of my lungs in case of possible blood clots.

I was vaccinated on a Monday and instantly felt awful. To say I felt drained is
an understatement. By the Thursday and Friday my chest felt as though someone
was sitting on it and I couldn’t even run in small stints with the dog. Friday
night I had crushing pain in my chest and my left arm went numb. I decided to
ride the pain out as I didn’t want to ‘burden the healthcare system’, but by
Saturday and Sunday I was having stabbing pains in the centre of my chest every
2 minutes for hours. My back felt terrible too, right where my lungs sit and
Monday morning I woke up to stabbing, throbbing pains in my heart, so I finally
decided to go to the hospital. Whilst I sat there, after I’d been triaged, 10
people came in in the space of around 20 minutes. EVERY SINGLE ONE OF THEM had
the exact same symptoms as me and all had had doses of the Pfizer Vaccine. I
could hear every conversation crystal clear, so I’m just relaying what I
heard. One guy had been in two weeks ago after his first jab and had been
referred to a cardiologist and was back again with the same pains in his chest –
he was 20!

Now let’s be clear, this is a vaccine I did not want. But having spent a massive
chunk of my life savings just living during these 260 days of lockdown and being
told I wouldn’t be able to work, being a part of society and just living without
being bullied, segregated and discriminated against……but I caved.

As I’m writing this, I have stabbing pains in my heart and left side of my boob
as well as the centre of my chest. I’m shaking with heart palpitations and feel
exhausted.

The doctor told me that I had had a reaction to the vaccine and many people have
come in with the exact same symptoms as mine after having had the Pfizer
Vaccine, and that a lot of side effects are coming out as it is a ‘new vaccine
in the very early stages’.

I was sent home after extensive testing and told to rest and take Panadol. Today
the pain has moved to the left side of my boob and mainly around my heart. I
went for a walk in the fresh air today and felt totally drained afterwards. Life
right now is really quite difficult and I am very scared!

So in the space of 8 days, I went from being a super fit and healthy non-smoker,
non-drinker, extremely active, to a situation with daily heart and lung pain
which ranges from crushing pain to stabbing, and the most extreme fatigue I’ve
ever felt. All because I went against everything I believe in, to stop people in
society shunning and judging me.

Please think again before you attack someone’s choices. If someone has vaccine
hesitancy, then don’t berate them. The risks of vaccine Injury are real and the
numbers of adverse reactions are probably way higher than we know. Just because
you were ok after your jabs, doesn’t mean others will be! Let’s hope I feel
better soon. But nobody can tell me that because there is not one shred of data
to say how this end for me!”
