My name is Jordan Vasquez, I am 26 years old, I am currently living in San
Francisco, California and I am a student at the moment. And I also compete in
martial art also. So I took the Pfizer vaccine the first dose on 2nd July and I
already kind a sort of feeling, effect next day on, the 3rd when I woke up on
Saturday morning. My chest closed and tie and just something wrong on the left
side of my chest. Two days after that it started feeling like tidier and bigger
and I was just like "huu maybe I just get thing checked out". So, I goes to the
ER and getting up in three packages, and Ultra sound after that and X-Ray and
then they diagnosed me with pericarditis. They told me they want to be sure
about it at first. they wanted to know if it was from exercise or mixed martial
art. At that time I told them it was mostly the shot because, you know, we were
training the whole year with hundred of people. Mixed martial art is a sport
that, you know, you can't wear a mask when you wrestler, grapple around. So, I
have been doing the whole year, I did not have problem, especialy with something
in my chest. I am definitively pro-vax for sure, I have taken every vaccine and,
just wanted to say that. This one I did have concern about how fast it was
made. It was not FDA approved. I think they wanted more studies behind it [...]
research more before vaccine the entire population. I think transparency is a
huge thing in our age right now. Definitively. More testing, more research, I
mean that kind of basis of science and how science it is. Research and studies
and putting different people in different kind of situation or environment. That
the whole basis of science.

