I didn’t see a reaction until one full month after my second dose of the Moderna
Vaccine. This is why I didn’t immediately connect the dots.

In June I started getting very dizzy and swaying on my morning walks. Then
chronic headaches. By Monday my vision started to go and my speech started to
slur, and that’s when I took myself to the ER. I thought I’d had a stroke or
seizure.

CAT scan came out fine and they suggested I see a neurologist. My first visit to
the neurologist is when I started to really think it was the Vaccine. They were
asking lots of questions about it.

Long story short, I ended up getting an MRI, EKG, EEG, and everything came back
normal. My neurologist said it’s probably adverse long term side effects and
it’ll just wear off. But to determine what exactly it was, I should get tested
for heavy metals from my PCP.

My PCP suggested, now that we know it was the Moderna Vaccine, what exactly is
the root of the problems…

He said there are 3 options:

\begin{itemize}

\item Test me for inflammation and see if the vaccine triggered an autoimmune
  disorder.
  
\item Test for heavy metals and see if the vaccine leaked a heavy metal.

\item If both tests come back fine, then it’s the Moderna Vaccine just not
  agreeing with your body for whatever reasons, and it could have simply just
  broke through the blood/brain barrier.
  
\end{itemize}

Both tests came back negative. And his response was….. he had no idea what to
do!

I have experienced everything from extremely tight chest and jaw pain, rapid
heart palpitations, intense migraines, ear pain, feeling like my head was going
to explode out of my body, short term memory loss, losing time and forgetting
who I am and where I’m going, a feeling of being brain dead and not being able
to think deeply or critically, tightness in my head, slurred speech and loss of
motor skills. Some days are good, some are not.

These Vaccine Injuries are real and are occurring more frequently than we think.
