Lorena is an RN of nine years, and spent 2020 working the frontlines. In January
2021 she received the Pfizer Vaccine and, since her second dose, it has been an
ongoing health battle and it’s now been almost one year since she has been
unable to work.

Below is her story, in her own words:

I have been dealing with symptoms that’s prompted many doctor’s visits, ER
visits, and hospitalizations. It all started after I received my 2nd dose of the
Pfizer Vaccine. I want to share my experience with hopes of bringing awareness
to what some of us have experienced from this Covid-19 Vaccine, and in doing so
will bring forth research to help us find treatment to relieve us of these side
effects we are suffering from.

On January 11th, I got my 2nd dose of Pfizer vaccine. Fifteen hours later, I
woke up with chest pain, fever, HR 160s, numbness, near syncopal episode, and
shortness of breath. I was hospitalized for 2 days and was told it was my immune
response to the vaccine. During this hospitalization I had labs, scans,
echocardiogram, IV fluids. A few labs were abnormal including my DDimer and
Lactic acid. CT chest was negative for PE. I was discharged home and my heart
rate was still high, but not as high. I also started to experience internal
tremors. Took it easy after my hospitalization, but then on Jan 30th, it
happened again. Same exact symptoms. This time I was hospitalized for 4 days. My
DDimer was higher so I had more workup done. They weren’t sure what was going
on, but I got put on propranolol since my heart rate wouldn’t go down this
time. This lowered my already low blood pressure so that got changed to Corlanor
outpatient by my cardiologist. Since then I have had multiple ER visits due to
high heart rate, near syncopal episodes, appointments with my pcp, cardiologist,
EP cardiologist, neurologist, gastroenterologist, pulmonologist and waiting for
my appointment with the autonomic neurologist at Stanford. I’ve had many tests
done which include echocardiogram, 2 week cardiac holter, stress test, labs,
loop recorder implanted, CTs, MRI, etc.

Since all this began my side effects have been and still are: tachycardia,
intermittent chest pain, PACs/PVCs, shortness of breath, internal tremors,
muscle spasms/twitching, constant vertigo/dizziness, headaches, brain fog, near
syncopal episodes, on and off loss of appetite(I’ve lost over 30 pounds since
January), fatigue, random intermittent joint pains, etc. My cardiologist in
Modesto says it’s possibly inappropriate sinus tachycardia, but I haven’t been
officially diagnosed. I will be seeing the EP cardiologist at Stanford in
November. I have in the past had vertigo and headaches but nothing as severe or
as consistent as this is debilitating now. I got COVID a few weeks ago and it
has definitely aggravated my side effects.

My next step is to maybe find a functional/naturopathic doctor to do extensive
labs and think outside the box because we still aren’t sure how to get relief of
these side effects.

I’m just so tired and frustrated of feeling this way. I haven’t felt like myself
since January 12th. My life has completely changed. I miss my life. I miss
feeling like me. I miss not feeling unwell every day. I hope that these side
effects some people are experiencing get researched and that answers are found
as to why and how to help with them.

Some recent Updates:

October 14, 2021 – I went to Stanford and was seen by a neurologist in their
Neuroscience Movement Clinic. The neurologist I saw is thinking I have POTS
and/or an autoimmune disorder of some sort that was triggered by the
vaccine. She ordered more labs which got done today. She referred me to her
colleague there at Stanford who is an autonomic neurologist to get tested for
POTS and have an EMG test done. She also referred me to a neuro-immunologist at
UCSF who is working with patients post vaccine who have long term side
effects. She thinks he can really help me figure some of this out. I’ll also be
starting vestibular therapy at Stanford and a new prescription was ordered to
help with the constant dizziness I’ve been since my current medication isn’t
helping.

November 15, 2021 – I had a consultation with an Autonomic Neurologist at
Stanford. He ordered for me to have autonomic testing for suspected POTS in
December as well as a repeat echocardiogram. For now, he told me to increase my
Corlanor dose, salt and water intake to help my low blood pressure and high
heart rate. Once we get results he will update the plan of care.

November 22, 2021 – I went over some labs with another specialist of mine and
got some overwhelming news on my health. My labs showed that my immune system is
not functioning optimally, my body has inflammation and I have several
illnesses/co-infections my body is currently trying to fight. I have Lyme,
active candida, reactivated Epstein Barr and mold. I will be starting treatment
for those soon

November 23, 2021 – Had constant chest pain, tachycardia and shortness of breath
so I went to the ER. CT was negative for PE.

November 24, 2021 – I saw neurologist and he went over my brain MRI results. He
is unsure what the lesion is that was found. This lesion was not there in my MRI
from February of 2020. The lesion is thankfully in the lateral optic area. I
will be having a repeat MRI with contrast this time in April 2022 to try to see
what it is and to see if it’s grown.”
