Shannon telling her story:

As I sat and thought about the vaccine, I was nervous and didn’t really want to
get it. After seeing everyone else get it and be okay, I decided it was okay to
receive it. On December 21st 2020 I received my first dose of the Pfizer and my
second dose on January 11th 2021.

Fast forward to March 27th 2021, I was at my normal weekend shift at my job as a
Respiratory Therapist, I texted my Husband that I did not feel well and that he
was my emergency contact in case something was to happen. So, I walked myself up
to the ICU where my co-workers sat. I asked one of them if they minded taking my
blood pressure, so she did. It was a little on the soft side.

Next thing I knew I was in the emergency room with nurses coming from all
over. I was told I was having seizures and that they needed to transfer me to a
larger hospital. I had a total of about 25 seizures while in my 3 hours in the
emergency room.

They got me out pretty quickly, and in the ambulance I went. I had three
seizures in about a 10 minute span. The EMT called the larger hospital I was on
my way to and was told to intubate me. As a Respiratory Therapist, that is not a
good thought for me.

The EMT asked to try one more thing and if it didn’t work then he would
intubate. Well the tranquilizer the EMT gave me worked (thank goodness). I was
sent to the larger hospital’s ICU and after two and a half days in the ICU, a
normal EEG with seizure activity and a normal MRI later, I was sent home.

After getting home, I went from being an independent and healthy 22-year-old to
being quite dependent on my Husband for care. Never in my life did I think a
shower chair would have to be used at my age. My Husband having to help wash my
hair because I was so weak, him physically having to hold me down so I didn’t
throw myself off the bed at 3 in the morning, or having to grab my arm and help
walk me around so I didn’t fall down.

After visiting the larger hospital, I went to two more even larger. Everyone
still giving me the same answers of unknown cause, unknown cause, and once again
unknown cause. After months and months of pain and suffering I threw a wild
pitch and, hoping for an answer, I went to see another Doctor. That Doctor did a
neurological panel and has pinned the cause of my seizures to Inflammation Of
The Brain caused as a reaction to my COVID-19 Vaccine.

If you were to walk into our house right now, you will see all tables are up
against the wall. I try to stay in safe areas of our house while my Husband is
gone to work making a living for us. At 22 years old: I can’t hold a full-time
job, I can’t drive, most days I cannot make it a full day of activity, it takes
all of me to sometimes make dinner.

Some days are okay and I have two seizures and some days you can’t count the
number I have because it is continuous all day.

The last 7 months have been absolutely terrible to live through, my body hurts
in ways I never knew it could. My Doctor says this is something I will probably
have to live with the rest of my life.

I have been quiet long enough in fear of the comments. I can’t speak for
everyone who has had reactions, but this is just my story. If you are
experiencing a reaction, you are not alone.


