Myrtle’s story told by her Granddaughter Ursula:

My beautiful, young at heart Grandmother, recovered from Covid last year and
came through it quite well. But like most people of her generation, she felt
obligated to get the Pfizer Vaccine to protect herself and others, as she had
been made to believe.

On 29th September 2021 she had her first dose. She complained about a sore arm
however seemed quite well. During October we noticed she was feeling increased
tiredness. She also complained of “battling with aches and pains” and “not
feeling herself”. There was a noticeable change in her and things she usually
enjoyed doing seemed a struggle.

Her second jab was due on 9th November and despite feeling not so great, she
went ahead.

On Wednesday 10 November my uncle went to see her in the morning. She was
struggling to breathe. He called an ambulance immediately. She complained that
her head was feeling hot and he provided her with a cold wet towel to put on her
head for some relief. He told her he had to go up the driveway and open the gate
for the ambulance. A few minutes later the paramedics made their way to her
bedroom. They found her unconscious on the bed and tried to revive her. They
started trying to resuscitate her and spent almost 20 minutes trying but
unfortunately, she had passed.

Cause of death has been confirmed as heart failure. My grandmother was still in
good health. She never had any heart issues. She suffered with Arthritis in her
legs however she was still full of life, living independently, playing piano and
cooking for family.

An autopsy has been refused and cause of death confirmed as heart failure.

The loss of our beloved grandmother and mother has been a shock and blow to us
all. We are devastated by her sudden loss that has left an irreplaceable void in
our lives.
