My name is Liz. I’m 36 and this is my story.

On March 22nd 2021 I received the first dose of Moderna Vaccine. I was 35 and I
haven’t been the same since!

The next day, less than 24 hours later, I started experiencing sharp chest
pains. At first, I didn’t think much of it; I was trying to ignore it thinking
it would go away. It became harder and harder to ignore, as now it was a
constant chest pain with sharp shooting pains.

On April 3rd, I felt my heart racing. My heart rate went up to 173 BPM, then my
left arm went numb and I felt my left hand tingling. I felt like I couldn’t
breathe. I thought I was having a heart attack. We called 911 and went to the
ER.

The doctor was asking me questions and I told her I’ve always been a healthy
person with no issues. The only new thing I had done was get the Moderna
Vaccine. Then she looked at me and said, “you’re having a reaction to the
Vaccine. I do not recommend you getting the second dose.” She said my heart was
fine, no heart attack and all tests came back clear. If I only knew that was
just the beginning….. but things were going to get a lot worse!

Four days later, I followed up with my doctor and was told it was probably just
acid reflux and anxiety. My doctor gave me medication for it, but she did not
believe it was the Vaccine. I know my body well; I knew something was very
wrong. Later that evening, my symptoms happened all over again. This time, my
face went numb and tingly and my heart shot up again. Then I went again to the
ER and this time I was admitted for 3 days. I was able to see a cardiologist and
had an echocardiogram plus further testing. Everything came back clear. I was
now experiencing anxiety attacks when I had never had anxiety before.

After I was discharged, I was so weak, fatigued and in pain. I had to leave my
home and move in with family to care for me as I couldn’t be alone. I was no
longer independent.

I’m now on a heart medication to lower my heart rate, but no one could tell me
why this was happening. My anxiety got so bad, I couldn’t sleep in darkness, I
couldn’t have the door shut, the shutters had to be open. Anything would trigger
an anxiety attack: loud noise, too much movement, too many people talking,
taste, smell, etc. Everything was so overwhelming for me I couldn’t even do
simple things like respond to a text message or make a call. I had never
experienced anything like this before. I felt like this was not my body, I had
no control over it. At this point, everyday brought a new symptom.

I began to have major pain in my ovaries so I went to urgent care where they ran
multiple tests and everything came back clear. Meanwhile, I was seeing a new
cardiologist who agreed to do further testing and put me on a holter monitor. I
could not understand what was happening to my body.

Then even more new symptoms began: tremors, twitching, shaking, nervousness,
muscle weakness, muscle spasms, burning sensation, sharp shooting pains,
dizziness, lightheaded, near fainting, shortness of breath, chest tightness,
elevated heart rate, insomnia, difficulty walking, with the right side of my
body experiencing pain which was so much worse.

My symptoms even included panic attacks, migraines, slurring my words, memory
problems, major brain fog, extreme fatigue, vision problems, tinnitus, right ear
pain, hair loss, hard time forming sentences or finding words, and couldn’t
concentrate. I thought I was dying.

Some days were so bad that my family had to spoon feed me, help me get dressed,
and help me shower.

I went back to the ER, again many more tests and yet, nothing, no answers to why
this was happening. At this point I was so discouraged I felt like I was not
going to get help. There were some doctors asking me if I do drugs. They told
me, “it’s all psychological, it’s all in your head, once you fix your mind
you’ll feel better, it’s just anxiety, it’s just stress, you just have to be
more positive.”

It’s sad how they make you feel like you are crazy. I was then diagnosed with
fibromyalgia and the doctor said it was just a coincidence this all was
happening after the vaccine but the vaccine was not the cause.

After seeing a neuromuscular specialist, she confirmed I wasn’t the only one
going through this. They had similar cases as mine who had their Vaccine earlier
Dec-Jan and who are still experiencing symptoms (this was in June when I was
only three months in).

I was now seeing a nurse practitioner for Psychiatry, all the anti-anxiety
anti-depression medication made things much worse. I was now experiencing all
the side effects from these medications. I went from taking zero medications to
try this one or that one, maybe this one will help you. Nothing was working for
me.

Then, one day, I began to get swelling in my face, throat, and entire right side
of my body. My right leg was so swollen and the pain was extreme. I made my way
back to the ER. They did an ultrasound to see if there was a blood clot and
everything came back clear. Still no answers.

After all my tests came back clear from cardiology, he suggested I have a tilt
table test done. That’s when I was diagnosed with POTS. I have also seen a
Rheumatologist and neurologist, but so far all tests have come back clear. Only
my ANA was borderline positive.

It is now September, five months later and I’m still experiencing symptoms.

Unfortunately many doctors don’t know how to treat or help me. Every provider I
see is different, they don’t know how long it will last, if it will go away, if
it’ll get worse, or be something permanent. All they say is ‘we don’t know what
the Moderna Vaccine can do, it’s too new to know’. It’s a very scary place to
be.

This experience has completely changed my life. I haven’t been able to work
since April and I’m on the verge of losing my job. Looking for doctors/
specialists, setting up appointments, going to appointments, following up with
doctors, and having extensive tests done has been a full time job. I’m also
doing therapy to cope with everything I’m going through. Some days are ‘good
days’ and some are ‘really bad days’.

Going from completely healthy and active to feeling homebound and sick with no
energy has definitely been a challenge and hard to cope with. My life has
literally changed overnight.
