I had the first vaccine January 22nd 2021. Four days later my fiancé thought I
was having a stroke, after I could not walk properly and kept falling over, so I
agreed to go to the hospital. They couldn’t find a clot. They set up an
appointment with a Neurologist. I waited a month to get into the Neurologist.

During this time, I went downhill. Every system was messed up. Walking, talking
, seeing straight, standing up , thinking, body shaking and couldn’t hold things
without dropping them.

I went to the hospital again during that time. They couldn’t figure it out. I
went from a fully functional Paramedic and Flight Attendant, to not being able
to be left alone, drive, shower or any of my daily living activities.

I had the Moderna One Shot. My neurologist said if I had another shot, I would
be dead.

The first Neurologist said I was an anti-vaxer, so I went to another
Neurologist.

My present Neurologist said he had no clue what to do , but he was going to try
and help me. I was put on Gabapentin, IV steroids, then had a week of IVIG and I
am still in Neuro-Therapy. He said it may have caused Guillain-Barré syndrome.

I had a scan on my legs by a vascular surgeon and they found blood clots. That
Doctor said he believes I had a lot of micro strokes. I’m still on blood
thinners. He was not surprised when I told him my story as he found multiple
blood clots in my right leg.

I got the shot. I was an essential worker. My son and I have had all of our
vaccines.

My fiancé took me to another Neurologist. I was his first case. Now he has at
least five other cases.

There, I have met others like me! We had all felt scared to tell others, alone
and terrified.

I may not be able to work again. No one helps us. There is nowhere to turn. Not
even social media. I’m better, but not back to where I was. I pray I get well.

Now, five year old innocent children will be told to take this Vaccine. Parents
are being blinded. I’m sure it has saved lives. But, get all the information
out, so people can make informed decisions. It makes me sick to think of the
outcome this could possibly have!
