Ben, an Aussie living in NZ, telling his story on 30th November 2021:

I am wanting people to know that this does happen to people. If it has happened
to you, then you should feel comfortable in speaking out so the health
professionals are more aware.

I would like to voice a fact that I understand everyone has individual views. I
do not wish to push anyone away from their own choice, I’m simply expressing my
current diagnosis /experience from being administered my first dose of the
Pfizer Vaccine.

Post injection I experienced some flu like symptoms. Headaches, cold sweats and
fatigue (which are common side effects). Then I began getting stabbing like pain
in the middle, slight left from the centre of my chest. They were dull but
definitely there. I had also lent on my left knee somehow causing a major
swelling in my leg. An abnormal amount of swelling as I have never had this
before.

None of this worried me till my knee started to swell quite badly and my chest
pain was becoming frequent. Miki had phoned Healthline and they told me to get
straight to hospital. We raced straight down and had all the testing/scans
carried out. Everything came up clear but was advised that my heart was possibly
being irritated by the Pfizer Vaccine. Prescribed medication, mostly for the
swelling in the knee, and headed home, only to return if symptoms worsened.

3 days later in the afternoon I began to experience constant chest pain and
shortness of breath, especially while laying down. After a few hours passed with
the pain, leg still swollen, I was back down to the hospital. Another lot of
tests done which came up clear and checked by a different doctor. I explained
all symptoms I was suffering and I was advised my heart was suffering from
Pericarditis from the Vaccine. Another lot of medication and sent on my way home
with this abnormally sharp chest pain.

I then saw my GP on the 6th day who ran the tests again and saw a slight
abnormality in my ECG results to confirm I was diagnosed correctly. Explaining
again, if symptoms worsen or veins begin to rise in my leg to then to reach out
for medical help.

The following morning my leg couldn’t hold my body weight and I had a varicose
vein popping out from behind my knee travelling 5cm upwards and sticking out by
1cm. We immediately called the ambulance and when they arrived the vein had gone
back to normal (unfortunately, in the panic, we didn’t get a photo).

Once again machines and tests carried out which were clear. The paramedics
notified my local Hospital and they simply said “If the vein is gone and his
vitals are clear we don’t need to see him”. The paramedics seemed concerned and
personally advised us to travel to a bigger hospital. So in the car we went for
an early morning trip of 2.5hrs.

Arriving at Emergency, tests were carried out which were all clear. I then had a
Dr X sit down and ask me why I was there. I explained ``my chest pain and
swollen leg''. She explained that she had looked over all my tests and they were
clear. As I tried to explain my worsening condition with new symptoms eg; the
vein in my leg and Pitting Edema (signs of blood clots) she cut me off saying
``your tests are fine, there is nothing wrong with you, you are probably
suffering these side affects from ``anxiety'' and there is nothing I can do for
you'', completely disregarding the fact that I was told if I experienced any of
these current symptoms to seek emergency help as this could possibly be a blood
clot.

I had to push asking for a D-dimer test and received a very quick ultra sound on
my leg.

Due to those test coming up clear Dr X told me the clot was most likely broken
down in my system, to stop all medication because my current diagnosis of
‘Pericarditis’ was incorrect and that nothing was wrong with me. I was sent home
with a new diagnosis of ``anxiety''. I was feeling very unsettled, without
answers and confused to how I could get so many different opinions... I didn’t
know who to believe!

This was the most humiliating experience to be told I was just anxious and that
my symptoms were in my head and my question at the time was, if she was so
certain that anxiety was the cause of these horrific symptoms, why didn’t she
help me resolve that issue? Dr X then told me to leave the hospital whilst in
pain.

I’m not the first person with this same experience.

The following day at an appointment with my GP, he again confirmed my ECG
results show different readings from each test which indicated Acute
Pericarditis. He confirmed that reactions like these are unexplainable, and are
happing to those who are healthy. I am unlucky and is an uncertain sort of
treatment because it’s a new product they are also dealing with. An honest
answer from a doctor means a hell of a lot more than being told you are
suffering from anxiety because they don’t know the answers. Dr X only looked at
my results at the current time and did not compare with previous ECG scans. Dr X
simply didn’t want to deal with my pain because she didn’t know the answer.

After a week long ordeal of 3 hospital visits, 2 ambulance calls and a call to
Healthline, I was still not taken in for monitoring, even with signs of blood
clotting!

I am immensely grateful for my GP and the ambulance service who listened to me,
believed me, and provided me with reassurance when all other systems failed me.

I am appalled with the New Zealand health system and Government. Restricting our
lives until we get this vaccine, and when we do and it goes wrong, most were
unwilling to listen or help. I did what was asked of me to protect myself and
others, and when it went wrong the system failed me hugely.

I am still experiencing chest pain and swelling in my knee but with medication
and rest I am recovering very slowly.

I am NOT ``anti-vax'' but I have personally chosen to voice my experience to be
transparent with everyone, as I believe this is hugely lacking and causing
immense uncertainty around the vaccines.

Share my story, as anxiety isn’t the issue.
