Dianna telling her Sons story:

I am the mother to a son in the United States Army. He is 21 years old.

November 2020, my son and daughter-in-law got sick, they both had COVID. Being
young and in the Army, he believed that getting the Pfizer Shot would help him
not get COVID or giving it to anyone else, so on May 24th, 2021 my son, with the
pressure of the Army, got his first Pfizer Shot. Things had been bad already
with heart palpitations, and shortness of breath after having Covid, but this
progressed to being much worse after the first shot.

Now it was numbness and weakness in his limbs, muscle spasms, breathing issues,
fainting, and seizures – all shortly afterwards.

Then on June 15th, he got the second shot, maybe this one would help overcome
the last one... Right... WRONG!

Now is has tics, he cannot hold a whole conversation anymore, my BRILLIANT son,
yep I’m biased, can no longer hold an entire conversation without stuttering his
way through the words.

This kid could articulate words at the age of THREE that other kids couldn’t, he
could read BEFORE he was in school! He was doing simple math at FOUR! Now he can
no longer walk a normal path, hold a normal conversation, or do what he wanted
to do for the rest of his life, DEFEND HIS COUNTRY!

I would like his story heard! He is tired of fighting, but I AM NOT! He is tired
of going to doctors and having them tell him “IT’S IN YOUR HEAD!” I am willing
to bet if he sued them, they wouldn’t think it was “IN HIS HEAD!” any longer. He
is tired of hearing he has “childhood trauma!” Him and his wife are tired,
me... I have a lot of fight left in me!

PLEASE help me get his story out! Please help me fight for him! Please help me
show him, HE ISN’T ALONE!
