I am currently battling an extreme adverse reaction from receiving the Johnson
and Johnson Covid-19 Vaccination.

I received the Johnson and Johnson Vaccination on September 17th at
12:00pm. After 10-15 minutes post vaccine, I began feeling the normal vaccine
reactions such as a head ache and nausea. I felt nothing of it and pushed
forward. After 30-45 minutes post vaccine, I felt I was on the verge of vomiting
and I began feeling tingling on the left side of my body from my foot up to my
buttocks, my left hand and left cheek. I rationalize it as the vaccine moving
through my body but I decided it was best for me to go home. I clocked off and
started my drive from Newberg to my home in Tigard.

On my way home, about an hour post vaccine, my father called to check in. At
that time I realized I was talking strange, my father even recognized the
change. I looked at myself in a mirror while at a stop light and noticed the
left side of my face has gone paralyzed. In extreme fear I began crying, told my
father I would let him know how things go but I was close to home and wanted to
make it safely so I hung up and continued home. Once I arrived home, the
tingling reached to a numb feeling and it became increasingly difficult to
walk. I laid down for a few hours hoping it would resolve but it hadn’t. I
informed my work and decided to head to the ER. I had my brother pick me up and
we made our way around 3:30pm.

They saw me right away for a possible stroke. Blood was taken and rushed to the
lab, I was taken in for a CT scan and was put into a room for a telehealth
appointment with a neurologist. After meeting with the neurologist and doing a
brief exam as well as reviewing my CT scan, he thought it was best to give me
medication to stop an active stroke, however, it had a very high death rate if
given to a patient who was not having a stroke. So I declined the medication and
we proceeded with an MRI.

Once the MRI was complete, the ER doctor and neurologist met and went over
everything. They came to a conclusion that it was not a stroke but was a complex
migraine and told me to take an Advil and it will be gone in the
morning. Frustrated with this diagnosis and inability to walk, I was sent home
with no assistance out of my bed and to my husbands car, mind you, I was
hobbling.

Waking up the next day, i could barely feel most of my left side, though my face
had mainly recovered, my smile was still crooked. I could feel tingling on my
right foot and I was scared it was spreading. My left arm and left leg were very
weak and the numb, jello sensation had moved to my left shoulder/collar bone and
I could not walk without assistance so I bought a cane. I took an Advil as
directed by the ER doctor and took a long nap at about 12, waking up around 4. I
visited a friends home with my husband to vent our frustration regarding the
last ER visit. We all decided it was best to call my PCP to inform him of the
new and worsening symptoms and asked for guidance.

He told us to go back to the ER to rule out Guillain Barre Syndrome which is a
common side effect with the Johnson \& Johnson Vaccine. So, we rushed back over
and arrived at 7:30pm but weren’t admitted till 11pm. Through the wait, I was
experiencing muscle spasms throughout my left side and a jello like sensation in
all my joints and major muscles. The ER doctors did a full exam and agreed that
there is significant weakness and drooping on my left side and some on the right
and that it would be best to be admitted to the main hospital to me monitored
and run further testing. I was assigned a room at midnight.

In short, for my 2 days spent in the hospital, my symptoms worsened and I failed
each neuro exam the nurse and doctors performed. I saw a physical therapist and
occupational therapist and they both urged me to seek inpatient rehabilitation
for a week or more to regain my strength again. However, I declined and said I
would seek physical therapy separately because I did not want to be away from my
family and pets during this emotionally stressful time.

I had another evaluation with a neurologist and he believed it was conversion
syndrome but since I was having signs of nerve damage, it was not a confirmed
diagnosis. My PCP recommended me seeking another neurologist outside of the
hospital to get nerve conduction testing to finally get a confirmed diagnosis
and get on the road to recovery.

So here I am today, September 24th, 2021. The weakness has spread further on my
left side to my neck and jaw, making it hard to eat and tiring to keep my head
up. I continue with physical therapy exercises the PT and OT gave me in the
hospital and am awaiting an appointment with the neurologist.

THE LEAD UP TO THE VACCINE... In April 2021, I caught COVID-19 and was
hospitalized for Covid Pneumonia where my right lung was full of fluid and no
antibiotic was working to rid the infection. It was truly scary and it took a
huge toll on my system that made it extremely challenging to recover and I still
have lingering respiratory issues from it.

Due to working in the medical field and governor Kate Browns mandate for health
care workers, I was required to be vaccinated, provide a medical exemption or
voluntarily leave my position at my company where I would be unable to collect
unemployment. I spoke with my primary care doctor regarding vaccine options with
my medical history in mind. We both came to an agreement that with having the
natural antibodies of COVID-19 and how my immune system reacts, it would be
dangerous to get the vaccination at this time.

My doctor predicted that if vaccinated with the MRNA vaccinations, and how they
disguise your normal cells into COVID cells, the natural antibodies and normal
cells would get confused and it could cause two possible different reactions –
1. I would have a severe auto immune reaction, making my cells attack
everything, even the healthy cells, resulting in another auto immune disease to
surface. Or 2. The stress the vaccine would put on my system when reacting with
the natural antibodies and my weakened immune system, would send a negative
signal to my brain, causing my brain to tell parts of my body to shut down, as
it tries to process and take care of the stress response that the vaccine is
putting on my cells and immune system.

MY MEDICAL EXEMPTION WAS WRITTEN BUT DENIED BY MY WORK! He wrote me a medical
exemption form and I swiftly turned it in over a week before the deadline. Then
I started running into issues……

The members of my works committee denied my medical exemption and agreed that
there was not a valid reason for me to not get the vaccine because there have
been cases of diabetics and immunocompromised people getting the vaccine and
being fine. However, on the CDC website, it states that there is not a lot of
research regarding immune compromised ones and folks who have auto immune
diseases, it states that it is in discretion of the person and their doctor
whether they deem it safe and at this time, it was not safe for me.

A member of the committee spoke in detail with my primary care doctor regarding
his reasoning behind granting me an exemption. However, his reasoning was not
enough and the member of the committee stated my doctor was giving
misinformation regarding the vaccines and was putting his patients at risk. In
addition to that, he consulted another physician from OHSU without my knowledge
and shared my conditions and story to this doctor and they decided (without ever
seeing me as a patient) I am fine to be vaccinated. Angered by this time, I went
and got antibody testing done to prove there is no need to receive a vaccine,
but was still denied the exemption.

I was stressed and upset and my hope was running low. I loved my job too much
and I did not want to put added stress on my co-workers in looking for a new
employee. I was given until September 17th to make my decision to either get
vaccinated or leave my position…..so, I caved and got vaccinated.

I received the Johnson and Johnson vaccination on September 17th at 12:00pm.
