I have been in Health Care for over 20 years until I received my first dose of
the Pfizer Vaccine.

Within two hours I got a severe headache, followed by flu like symptoms over the
next three days. On the third night, I lost the use of my left leg. When I woke
up the next morning both of my legs were gone. I couldn’t move them or control
them. Within 30 minutes, seizure like activity started which turned into full
body convulsions.

I have lost the use of my legs three times since January. Eleven months later, I
am still dealing with tremors, fatigue, muscle weakness, pain, headaches,
tingling, numbness, burning sensations all over my body, brain fog and memory
loss.

I lost my career in Health Care. I didn’t drive for 7 months after my Vaccine. I
do not go out in public much. I am scared of the convulsions starting as it has
happened before in public, and it scares everyone around me. I can’t go up and
down stairs without my legs shaking to the point I cannot control them. I try to
be hopeful but, I am not sure at this point if my life will ever be the way it
used to be. I try to remain positive and supportive of others with these adverse
reactions but I must be truthful with myself and accept things as they are.

I was hospitalized for 5 days. I have had around 60 doctors office visits and
travelled 5200 miles for failed treatments. I’ve spent my life savings on these
treatments and visits. I am still undiagnosed.

My Adverse Reactions have been reported to Pfizer, the CDC, FDA, and the NIH
Louisiana State Health Department. To date I have received no substantial
response from anyone.

If you are unfortunate to end up like us, Vaccine Injured, you are totally alone
trying to figure out your treatments. There is no proper healthcare for
you. Many doctors completely hide your symptoms and cover them up. They will not
admit or address any of your Vaccine Adverse Reactions.
