I started to have blurred vision and couldn’t breathe properly, shaking all over
and massive hand pain. The next day in the morning I was very weak and still had
the pain on my hand but felt better. Third day started with extreme dizziness,
nausea, light fainting, derealisation, lost balance, vomiting, electric zaps
sensations, pins and needles, head pressure, chills, spine pressure and numbness
all over (that has lasted for more than 4 months).

It was getting worse in intensity daily. After the day 10 I was fine and back to
myself. I thought, that it is done, all good. But right before my period, it all
started again, more intensely, and since, I have a flare around my monthly
cycle.

The symptoms changed over time, some better some worse. I still have twitching
muscles, head pressure, and chills, burning feelings, eyes pain, all over
weakness in muscles, pins and needles and blurred vision. I am intolerant to
sport. If I do too much I feel sick straight away. I have some memory loss and
stuttering in my speech. I forget things easily and this never happened before.

Every day is different as you never know what you will feel. I try to stay
positive and push through this battle but sometimes I feel hopeless when the
pain is unbearable.

I have had a brain MRI and apparently is all clear. Have been twice to emergency
and they didn’t know how to help me as the investigations were all good. One of
the doctors said to me they don’t have a clue yet what’s happening, all
suggested to not have the second one but I don’t have any notification of this.

I have been referred to a Long-Haul Clinic for months now and nothing. Had an
appointment with one of their neurologist but they declined me. GP doesn’t help
me at all, pointing to the fact that I have months to wait to be seen, so they
don’t refer me.

No help at all from any medical community. No treatment and no diagnosis.

I’m improving but extremely slowly and every day is a challenge, or a new
symptom appears, mostly neurological.

From a bubbly and joyful woman, I barely function or socialise. It is hard to
explain to someone what you feel if they didn’t experience this. My faith In God
helps me so I have hope despite of this battle. I would love to have a chance,
for my peace of mind, to have more investigations and more answers.

Took my life away. I miss myself. I miss my light. I am strong and keep pushing,
I won’t let them win. I nearly died, I can say, but is not my time yet, in line
to fight and we will win.

I feel that I live in someone else’s body. I am not myself and I deeply regret
that I took this Pfizer Vaccine.
