In Scott’s own words:

I feel it necessary to share my story with you all in an attempt to help educate
people about the potential negative side effects associated with the Pfizer
COVID-19 vaccine, so that people are more aware of the associated risks of
having the vaccine and as a result can make a more informed decision as to
whether they should have the vaccine or not.

I was an extremely fit and healthy male having dedicated most of my life to
training and maintaining my physical fitness.

In late July all healthcare workers we’re told that as of the 4th of August 2021
we were required to have our first COVID-19 vaccination or else our employment
would be affected. I was given an ultimatum, get the jab or lose your job! Up
until this directive I had made the personal choice to abstain from having the
vaccine due to the staggering number of deaths and illness that are directly
related to the mass administration of a non-FDA approved vaccine. I feel that it
is our human right to be able to decide what we put in our bodies.

On the 3rd of Aug 2021 whilst on duty my company paid for my taxi to the
COVID-19 vaccine clinic to receive my first jab. Within hours of receiving the
vaccine I felt dizzy, disorientated, I had a headache and my heart was
pounding. In the days that followed my symptoms worsened and as a result I was
not able to work. I was experiencing stabbing chest pain, shortness of breath
and severe headaches, these were just the serious symptoms and not the more
common flu like symptoms that we are told to expect.

On Sunday the 8th of August I was struggling to breathe and having serious
intermittent chest pain. After completing my shift at 2:00 pm I booked in to the
emergency department to be assessed. I was informed that my blood results had
returned positive for Blood Clot. After extensive testing it was determined that
the clot had likely already dispersed and I was diagnosed with pericarditis,
given a prescription for multiple medications that I will now need to take every
day for the next 1 to 3 months. It is unclear whether I will ever make a full
recovery from this. I would like to add that I had no pre-existing medical
conditions prior to receiving the vaccine.

I had a full check-up of my heart including an echocardiogram only 12 months
prior and was told that I am in perfect health. I now suffer from serious chest
pain and shortness of breath every day. I cannot do any of the things that I
enjoy such as going to the gym, or any form of physical exercise that will
increase my heart rate as this can exacerbate my condition.

What the future holds for me is unclear. So, for those of you that are also
being coerced into having a vaccine against your wishes please take the time to
consider all aspects of this decision and how this could affect your life and
those you love.

