He died less than 12 hours after receiving the Pfizer vaccine, suffering a fatal
seizure. Luke’s mother Tricia Garrett tells her sons story:

“Luke had muscular dystrophy and had been shielding for around a year so was
‘excited’ when his turn to get a vaccine meant he could finally ‘live his life’.

But he died in the early hours of the morning the day after getting the jab,
leaving his family ‘devastated’ and desperate for answers.

The Medicines and Healthcare products Regulatory Agency (MHRA) are investigating
Luke Garrett’s death – but there is no evidence of the jab causing seizures.”

She described Luke to have ‘foam coming out of his mouth’ during his seizure –
and told how she gave her dying son CPR as they waited for paramedics to arrive.

“He used to have support workers who came in three times a week, he also had
high-functioning autism and needed support for that, but he cancelled it all
because he was that scared of Covid. He was excited about going to get his Covid
jab, being able to return to some kind of normality.

It wasn’t even 12 hours after his Covid jab that he died. His whole body was in
horrendous pain and he had a really high temperature. Normally with his
condition, his legs can end up in pain, but this was very different.

Before he died, the arm he received the injection in was really painful. He then
suffered a seizure, which had never happened before. He started to fit and there
was foam coming out of his mouth”.

She believes her son would still be alive if he didn’t get the Pfizer Covid Jab
that day.

“I phoned 111 about 1am and told them somebody needs to come out. I thought he
needed a muscle relaxant to help with the terrible pain. A nurse told me they
would send someone out within two hours, she was really detailed with
everything, she asked about temperature and muscle pain. They promised they
would call back within the two hours, but no one called. Instead, I received a
call at 4am to ask if Luke still needed help. I just told them, ‘My son is
dead!'”

Luke was just ten days away from celebrating his 21st birthday.

Mrs Garrett – who lives with her husband Shaun, 49, and 18-year-old daughter
Anna – told how she gave her son CPR while they waited for paramedics to arrive.

She added: “I was giving him CPR on his chest whilst on the phone to 999. The
paramedics didn’t have a clue what had caused it, they just tried to give him
adrenaline but there was nothing more they could do. Our son was fit and well,
doctors used to say he was one of the better patients they had seen.”

The post-mortem showed his heart was in a perfect condition. He had never had a
seizure before.

A spokesperson for MHRA said: ‘We are saddened to hear of this loss, and our
thoughts are with the family.’

