I received the J\&J Vaccine on April 5,2021. Since then, I’ve been horribly
sick. When it first started, it was a normal day, I started to feel dizzy. I got
to the ground and tried to focus on my breathing. Suddenly my whole body locked
up and my entire body started convulsing. I couldn’t get up. After maybe 10
minutes of that I regained ability to move and started vomiting. My Fitbit read
that my heart rate was 170 bpm.

I called for help right away. Since that day, I have severe Tachycardia and
Hypertension. I take Metoprolol around the clock to help manage my BP and heart
rate. I’ve seen my heart rate as high as 180 bpm and my BP as high as 180/120,
and that was with medicine in me. I’m also on a second BP med and it helps a
little. I have bad chest pain all the time and heart palpitations. I have these
terrible “spells”, as I call them, where my heart rate is out of control and
it’s the worst feeling ever. They can last from hours to days. I have had to go
to the ER 5 times over my heart rate being too high, even with beta blockers in
my system.

My body now has trouble regulating my blood sugar. It drops for no reason and
sometimes it gets too high. My memory has been affected. I have panic/anxiety
attacks that can last days at a time. I’m on 2 different anxiety medications now
and they don’t help. I have had regular periods ever since I was 12 years old
and I haven’t had a period since I received the J\&J Vaccine.

It’s been 7 months now with no menstrual cycle. I can’t regulate my body
temperature. I’m hot alI the time. I can’t tolerate heat what-so-ever. I get
very dizzy and weak. I also have a neurological “tic” I guess you’d call it, my
head shakes back and forth sometimes and I have uncontrollable body movements.

I used to have great energy and now I’m SO tired all the time. I have severe,
debilitating inflammation throughout my whole body. It affects every joint I
have. I have shortness of breath and now I get headaches.

Since I’ve been sick, I have had to quit caffeine, smoking, and alcohol. I’ve
had to manage my stress. All of those things trigger my bad spells. Doctors have
told me I’m not to drive anymore and I can no longer physically exert
myself. Even trying to walk up a slight hill makes me out of breath and I feel
like I’ll pass out.

I was hospitalized for a week at a mental hospital after going to the ER because
I had a 4 day long panic attack and I couldn’t get my heart rate under control.

I was a healthy, 22-year-old woman before this Vaccine.

It’s been 7 months. I’m tired of suffering and I want my life back. I’ve seen a
bunch of different doctors and absolutely no answers.
