Aged 49 Years Old, Kerry’s Story told by her Niece Jodie:

We want to share with you my Auntie Kerry’s story who lives in the United
Kingdom.

She had her first dose of AstraZeneca on the 1st April 2021, and started with
symptoms on the 8th April 2021. She started with really bad pains in her head
and eyes. She rang the doctors and they told her to get an eye test but she
couldn’t get one for a week later. She told the doctors she’d had the
AstraZeneca a week ago but the said nothing more about it.

On the Friday she was no better so went for a Covid Test and that was returned
negative.

Saturday she was still the same so she rang 111, and A\&E rang back within 10
mins saying she needed to go in to hospital ASAP.

She then, she went through CT scans which revealed the blood clot in the vein in
her head. Her platelets dropped to only 19 and as they were trying to raise them
slowly enough not to cause more clots but it sadly caused a bleed on her brain
that caused a massive stroke. This caused brain damage and some loss of sight in
her left eye.

She then went under life saving surgery to remove part of her skull to help
reduce the swelling. We were told she had less than 40\% chance of pulling
through. Luckily she did.. but sadly she has lost the use of her left hand side.
At the moment it’s extremely slow progress. We’re waiting for the swelling to go
down before they can put the part of the skull they removed back in

She’s having physiotherapy Monday to Friday but can only manage an hour a day
due to it making her so tired.

She was a healthy happy 49 year old, but now we don’t know what the future
holds.

