The first dose produced no reaction. It was easy and painless and I almost
forgot I had gotten it. On whim, I decided to get the booster dose. I figured
the first one gave me zero reaction, and it’s not an mRNA Vaccine, so I expected
the second dose to be easy as well.

The day I got the Booster I was fine. About the third day I felt tired, but
that’s not too unusual considering my sleep schedule. The fourth day I woke up
and it felt like my right ear was clogged. Normally when that happens, I’m able
to make my ears pop, but this time I couldn’t. It also felt like my ear was
really full or something was in it. I thought it could be allergies because they
are going crazy for everyone right now, but something about this felt different.

The next few days I noticed that the fullness and clogged feeling wasn’t getting
any better at all. It seemed to be getting worse.

The next day I realized I couldn’t hear almost anything out of my right ear. Now
it’s been 8 days and I am functionally deaf in my right ear. I’ve taken a dozen
hearing tests and all of them say I have significant hearing loss.

In addition to that, on day 7 I started to get this horrible sensation almost
like i’m receiving an electric shock into my brain. The first time it happened
was disorienting, but I was sitting down so it wasn’t bad. The next time it
happened was when I was walking my dog. It was extremely disorienting and it
made me lose my balance and almost fall over.

I can’t really listen to music anymore because I can’t hear it. I can’t have a
normal conversation because I have to keep asking people to repeat
themselves. If there’s any sort of background noise, I for sure can’t hear what
anyone says. The brain zaps happen multiple times a day, but the effects of
those are thankfully short lived.

I’ve been referred to an ENT, as the doctors I’ve spoken to won’t touch the
illness because I’ve said it was related to the J\&J Vaccine!
