Georges Story shared by his wife Janet:

I begged my husband to stay away from the Vaccines. Indeed, he found himself
constantly consoling me the night before his injection. I pleaded with him to
look at the evidence I had uncovered that showed that this was still
experimental. The phone call from the doctor did not mention that it was still
being “studied” and would be until 2023, but he NHS website did. I had the site
up on my computer screen, he would not look, called me a conspiracy theorist and
laughed.

He had COPD and all he wanted to do was to stay alive. He was the love of my
lives (yes, I believe we went back through many life times) and all I wanted was
to keep him alive. He bought the hype about the virus and that it would kill
him. I didn’t. It was the only thing we argued about in the last 15 months of
his life.

His injection was given at our local surgery as he was classed as “shielding”
which meant that he was offered the jab there rather than at a “hub”. The first
was given by a nurse who said the only side effects were “a headache, pain in
the arm and sometimes mild flu symptoms”. Nothing was said about the possibility
of blood clots, stroke, heart attack or death. “It’s safer than taking your
chances with the virus”. The virus that killed 3 in 8,000 people world wide and
whose main victims were, in the UK, over 84 where life expectancy is 82.

He did have a headache, he did have slight flu symptoms for two nights. I asked
him to let me log it on the MHRA Yellow Card system and he would have none of
it.

Then came time for the second one. By this time, April, many countries in Europe
were questioning the use of this so called Vaccine and I again suggested he read
some of the “alternative news” before he went ahead. Again he assured me he was
going to be fine, he just wanted to stay alive. Our life was all about having
fun and we had a long schedule of touring planned for the summer.

A few days after the second jab he cut his hand and the blood dropping on the
floor looked to be separating, like oil from water. I made a note to photograph
it after I had sorted out the cut on his hand. He cleaned it up before I got the
chance. I have since found out that this is a sign of thrombosis.

Two weeks later he woke up during the night with an itchy rash on his leg, the
itch was so bad it kept him awake. I suggested we record it in the MHRA Yellow
card but he said it was “just a rash” and the jab was a couple of weeks ago. No
dots to connect here.

Five weeks after his second jab, I’m not going to call it a Vaccine, because
it’s not, I found him dead. I had gone to waken him because we were going away
for the night, so I went from a total high to the bottom being pulled from my
world in a nano second. This was on 19th May, 2021.

When I found him he had clearly been dead for a long time, the body was stiff,
blue and ice cold, still I begged him to come back to me. 47 years of love,
ripped from me.

The house became a bustle of police, one paramedic was the first to arrive, then
the police, as is the case with a sudden death at home. They realised that he
had an air rifle licence, more police arrived, then my family and within an hour
of me finding him our family doctor was on the phone telling me that there would
be no post mortem because it would be too “traumatic” for me. I was already
traumatised and his words really meant nothing to me at that stage, all I wanted
was to wake up and find this was a nightmare. The doctor said he was declaring
it a heart attack.

I was told that he had hit his head, his face was in a pool of blood, the carpet
is still stained. My first thought was that there has to be a murder
investigation at least, surely, I was alone with him in the house, surely they
had to investigate that? No.

In the days that followed we received the death certificate with “possible
Myocardial Infraction”. I was convinced that the Vaccine had killed him. A
neighbour, who is a doctor, agreed with me and said he thought that the lack of
post mortem was a “cover up”. My husband was only 65, sudden death at home, no
Covid outbreaks at this time, he had no symptoms of even a cold…

The MCCD was also full of fabrication. The doctor said he had been in
attendance, he wasn’t, it was a telephone call with a paramedic. He said my
husband had diabetes for 33 years, he had it for 54 years. He said he was found
at 9am, he was found at 11am.

The doctor called me six days later to “check up on me”. By this time I was
furious that they had killed the love of my life, I mean, how am I a supposed to
carry on living when he is not? I asked the doctor what he was thinking about
(my language may have been coloured by my inner Irish Navi), giving AstraZenica
to a man who was on blood thinners. He said that “they had done their best given
the information at the time”. In the end I called him a murdering whatsit and
put the phone down.

I am still furious that they took my soul mate from me.

The last time I’d seen him was a couple of hours before he died. He appeared to
be having a hypo (low blood sugar) and I helped to bring him right. He said “I’m
sorry, I think I really fucked things up”. I thought he meant because he would
need to sleep late the following morning and assured him that we could go away
if he felt up to it and if he didn’t it was ok, his health comes first. Now I
don’t think that’s what he meant. Now I believe he knows that they murdered him!

George Abernethy 3 March 1956 – 19 May 2021

